---
title: "Landscape Appearance"
author: "Andrew Antaya"
date: "June 20, 2019"
output:
  html_document: 
    theme: readable
    toc: yes
    toc_depth: 5
    fig_caption: yes
  word_document:
    toc: yes
---

# Setup

First, let's remove all objects from the environment to start fresh each time.

```{r clear environment}
rm(list = ls(all = TRUE))
```

```{r setup environment}
source("environment.R")
```

# Load Data

```{r Load Landscape Appearance Database}
landscape_appearance_database <- readr::read_csv(
    file.path(
        getwd(), "data", "landscape-appearance", "heber",
        "landscape-appearance-database.csv"
    ),
    col_names = TRUE, na = c("", " ", "NA")
)
print(landscape_appearance_database)
```
## 2018

The 2018 data had some special considerations that we had to clean up before we could bring it in for analysis. We re-created the data from a summarized table to make it consistent with data from the following years.

We then can read in this cleaned up data in the form of tibbles from another R Markdown document.

```{r }
source_rmd("2018-heber-landscape-appearance.Rmd")
```

Then we can calculate summary stats for each tibble.

```{r}
BKS_2018_stats <- BKS_2018_la_tibble %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")

BKS_2018_stats
```

```{r}
BRL_2018_stats <- BRL_2018_la_tibble %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")

BRL_2018_stats
```

In 2018, we took 52 samples at the Black Canyon South site, and 62 samples at the Bear site. It's hard to say why we took 10 more samples at the Bear site, my guess is that we lost track of how many samples we had taken a did an extra 10.

To get average percent utilization, we sum the "product" column and divide it by the number of samples taken at each site.

Average percent utilization for Black Canyon South 2018.

```{r add site and year to BRL 2018 stats}
BRL_2018_stats <- BRL_2018_stats %>% 
  add_column(Site = "Bear", Year = "2018", .before = "variable")

BRL_2018_stats
```

```{r add site and year to BKS 2018 stats}
BKS_2018_stats <- BKS_2018_stats %>% 
  add_column(Site = "Black Canyon South", Year = "2018", .before = "variable")

BKS_2018_stats
```

```{r row bind 2018 stats}
heber_2018_stats <- dplyr::bind_rows(BRL_2018_stats, BKS_2018_stats)

heber_2018_stats
```

```{r add confidence intervals bounds 2018}
heber_2018_stats <- heber_2018_stats  %>% 
  dplyr::mutate(lower_95 = mean - ci) %>% 
  dplyr::mutate(upper_95 = mean + ci)
print(heber_2018_stats)
```

### Plot 2018 Landscape Appearance

```{r 2018 Heber Landscape Appearance Figure}
ggplot(heber_2018_stats, aes(fill = Site, x = Site, y = mean)) +
  geom_col(width = 0.75) +
  guides(fill = "none") +
  labs(title = "Heber Landscape Appearance 2018", caption = "n = number of samples") +
  ylab("Average % Utilization ± 95% CI") +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
  geom_errorbar(aes(ymin = (mean-ci), ymax = (mean+ci)), position = position_dodge(0.5), width = 0.25) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 0, r = 0, b = 10, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 10))) +
  # add % utilization values above the  error bars
  # round the mean value using significant figures
  annotate(geom = "text", 
           x = 1, 
           y = (heber_2018_stats$mean[1] + heber_2018_stats$ci[1] + 7), 
           label = paste0(signif(heber_2018_stats$mean[1], 2), "%")) +
  annotate(geom = "text", 
           x = 2, 
           y = (heber_2018_stats$mean[2] + heber_2018_stats$ci[2] + 7), 
           label = paste0(signif(heber_2018_stats$mean[2], 2), "%")) +
  # add sample sizes to each bar
  annotate(geom = "text",
           x = 1,
           y = (heber_2018_stats$mean[1] / 2),
           label = paste("n", "=", heber_2018_stats$n[1], sep = " "),
           size = 3) +
  annotate(geom = "text",
           x = 2,
           y = (heber_2018_stats$mean[2] / 2),
           label = paste("n", "=", heber_2018_stats$n[2], sep = " "),
           size = 3)

# ggsave("2018-Heber-Landscape-Appearance-95CI.jpg",
#    path = paste0(getwd(),"/figures", "/landscape-appearance"))
```
## 2019

### White Mountains

```{r White Mountains 2019 Landscape Appearance Stats}
white_mountains_2019_stats <- landscape_appearance_database %>%
  dplyr::filter(Year == 2019) %>%
  dplyr::filter(Site == "Wildcat" | Site == "Boggy") %>% 
  dplyr::group_by(Site) %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common") %>% 
print(white_mountains_2019_stats)
```

```{r Add Confidence Intervals White Mountains 2019}
white_mountains_2019_stats <- white_mountains_2019_stats  %>% 
  dplyr::mutate(lower_95 = mean - ci) %>% 
  dplyr::mutate(upper_95 = mean + ci)
print(white_mountains_2019_stats)
```

```{r Plot White Mountains 2019 Landscape Appearance}
ggplot(white_mountains_2019_stats, aes(fill = Site, x = Site, y = mean)) +
  geom_col(width = 0.75) +
  guides(fill = "none") +
  labs(title = "White Mountains Landscape Appearance 2019", caption = "n = number of samples") +
  ylab("Average % Utilization ± 95% CI") +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
  geom_errorbar(aes(ymin = (mean-ci), ymax = (mean+ci)), position = position_dodge(0.5), width = 0.25) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 0, r = 0, b = 10, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 10))) +
  # add % utilization values above the  error bars
  # round the mean value using significant figures
  annotate(geom = "text", 
           x = 1, 
           y = (white_mountains_2019_stats$mean[1] + white_mountains_2019_stats$ci[1] + 7), 
           label = paste0(signif(white_mountains_2019_stats$mean[1], 2), "%")) +
  annotate(geom = "text", 
           x = 2, 
           y = (white_mountains_2019_stats$mean[2] + white_mountains_2019_stats$ci[2] + 7), 
           label = paste0(signif(white_mountains_2019_stats$mean[2], 2), "%")) +
  # add sample sizes to each bar
  annotate(geom = "text",
           x = 1,
           y = (white_mountains_2019_stats$mean[1] / 2),
           label = paste("n", "=", white_mountains_2019_stats$n[1], sep = " "),
           size = 3) +
  annotate(geom = "text",
           x = 2,
           y = (white_mountains_2019_stats$mean[2] / 2),
           label = paste("n", "=", white_mountains_2019_stats$n[2], sep = " "),
           size = 3)
# ggsave("2019-White-Mountains-Landscape-Appearance-95CI.jpg",
#   path = paste0(getwd(),"/figures", "/landscape-appearance"))
```

### Heber

```{r Heber 2019 Landscape Appearance Stats}
heber_2019_stats <- landscape_appearance_database %>% 
  dplyr::filter(Year == 2019) %>%
  dplyr::filter(Project == "Heber") %>% 
  dplyr::group_by(Site) %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")
print(heber_2019_stats)
```

```{r Add Confidence Intervals Heber 2019}
heber_2019_stats <- heber_2019_stats  %>% 
  dplyr::mutate(lower_95 = mean - ci) %>% 
  dplyr::mutate(upper_95 = mean + ci)
print(heber_2019_stats)
```

We need to convert the Site from a character to a factor so that it will plot in the correct order using ggplot2.

```{r Convert "Site" from Character to Factor Heber 2019}
heber_2019_stats$Site <- heber_2019_stats %>% 
  pull(Site) %>% 
  forcats::as_factor() %>% 
  forcats::fct_inorder()
print(heber_2019_stats)
```

We are ready to generate a plot for Heber 2019.

```{r Plot Heber 2019 Landscape Appearance}
ggplot(heber_2019_stats, aes(fill = Site, x = Site, y = mean)) +
  geom_col(width = 0.75) +
  guides(fill = "none") +
  labs(title = "Heber Landscape Appearance 2019", caption = "n = number of samples") +
  ylab("Average % Utilization ± 95% CI") +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
  geom_errorbar(aes(ymin = (mean-ci), ymax = (mean+ci)), position = position_dodge(0.5), width = 0.25) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 0, r = 0, b = 10, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 10))) +
  # add % utilization values above the  error bars
  # round the mean value using significant figures
  annotate(geom = "text", 
           x = 1, 
           y = (heber_2019_stats$mean[1] + heber_2019_stats$ci[1] + 7), 
           label = paste0(signif(heber_2019_stats$mean[1], 2), "%")) +
  annotate(geom = "text", 
           x = 2, 
           y = (heber_2019_stats$mean[2] + heber_2019_stats$ci[2] + 7), 
           label = paste0(signif(heber_2019_stats$mean[2], 2), "%")) +
  annotate(geom = "text", 
           x = 3, 
           y = (heber_2019_stats$mean[3] + heber_2019_stats$ci[3] + 7), 
           label = paste0(signif(heber_2019_stats$mean[3], 2), "%")) +
  # add sample sizes to bars
  annotate(geom = "text",
           x = 2,
           y = 0,
           label = paste("n", "=", heber_2019_stats$n[2], sep = " "),
           size = 3) +
  annotate(geom = "text",
           x = 1,
           y = (heber_2019_stats$mean[1] / 2),
           label = paste("n", "=", heber_2019_stats$n[1], sep = " "),
           size = 3) +
  annotate(geom = "text",
           x = 3,
           y = (heber_2019_stats$mean[3] / 2),
           label = paste("n", "=", heber_2019_stats$n[3], sep = " "),
           size = 3)

ggsave("2019-Heber-Landscape-Appearance-95CI.jpg", 
   path = paste0(getwd(),"/figures", "/landscape-appearance"))
```

## 2020

### Heber

```{r Heber 2020 Landscape Appearance Stats}
heber_2020_stats <- landscape_appearance_database %>%
  dplyr::filter(Year == 2020) %>% 
  dplyr::filter(Site != "Wildcat" | Site != "Boggy") %>%
  dplyr::group_by(Site) %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")
print(heber_2020_stats)
```

```{r Add Confidence Intervals Heber 2020}
heber_2020_stats <- heber_2020_stats  %>% 
  dplyr::mutate(lower_95 = mean - ci) %>% 
  dplyr::mutate(upper_95 = mean + ci)
print(heber_2020_stats)
```

```{r Convert "Site" from Character to Factor Heber 2020}
heber_2020_stats$Site <- heber_2020_stats %>% 
  pull(Site) %>% 
  forcats::as_factor() %>% 
  forcats::fct_inorder()
print(heber_2020_stats)
```

```{r Plot Heber 2020 Landscape Appearance Figure}
ggplot(heber_2020_stats, aes(fill = Site, x = Site, y = mean)) +
  geom_col(width = 0.75) +
  guides(fill = "none") +
  labs(title = "Heber Landscape Appearance 2020", caption = "n = number of samples") +
  ylab("Average % Utilization ± 95% CI") +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
  geom_errorbar(aes(ymin = (mean-ci), ymax = (mean+ci)), position = position_dodge(0.5), width = 0.25) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 0, r = 0, b = 10, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 10))) +
  # add % utilization values above the  error bars
  # round the mean value using significant figures
  annotate(geom = "text", 
           x = 1, 
           y = (heber_2020_stats$mean[1] + heber_2020_stats$ci[1] + 7), 
           label = paste0(signif(heber_2020_stats$mean[1], 2), "%")) +
  annotate(geom = "text", 
           x = 2, 
           y = (heber_2020_stats$mean[2] + heber_2020_stats$ci[2] + 7), 
           label = paste0(signif(heber_2020_stats$mean[2], 2), "%")) +
  annotate(geom = "text", 
           x = 3, 
           y = (heber_2020_stats$mean[3] + heber_2020_stats$ci[3] + 7), 
           label = paste0(signif(heber_2020_stats$mean[3], 2), "%")) +
  annotate(geom = "text", 
           x = 4, 
           y = (heber_2020_stats$mean[4] + heber_2020_stats$ci[4] + 7), 
           label = paste0(signif(heber_2020_stats$mean[4], 2), "%")) +
  # add sample sizes to bars
  annotate(geom = "text",
           x = 1,
           y = (heber_2020_stats$mean[1] / 2),
           label = paste("n", "=", heber_2020_stats$n[1], sep = " "),
           size = 3) +
  annotate(geom = "text",
           x = 2,
           y = (heber_2020_stats$mean[2] / 2),
           label = paste("n", "=", heber_2020_stats$n[2], sep = " "),
           size = 3) +
  annotate(geom = "text",
           x = 3,
           y = (heber_2020_stats$mean[3] / 2),
           label = paste("n", "=", heber_2020_stats$n[3], sep = " "),
           size = 3) +
  annotate(geom = "text",
           x = 4,
           y = (heber_2020_stats$mean[4] / 2),
           label = paste("n", "=", heber_2020_stats$n[4], sep = " "),
           size = 3)
# ggsave("2020-Heber-Landscape-Appearance-95CI.jpg", 
#    path = paste0(getwd(),"/figures", "/landscape-appearance"))
```

## 2021

We need to create a variable called "Territory" that displays if a site is "On" territory, i.e., within the Heber Wild Horse Territory. We'll create a new column called "Territory" and use an `if_else()` statement to determine if a given site falls within a territory. 

Note that this function will also label all of the White Mountains sites as "Off" territory, and while technically correct, they are off the territory, it might make more sense to label the White Mountains data as "NA". 

```{r Add "Territory" Variable Using Site List}
landscape_appearance_database <- landscape_appearance_database %>%
  mutate(Territory = if_else(
            Site == "BKN" | Site == "BRL" | Site == "BKS" | Site ==
                "GETPBG" | Site == "SHPT" | Site == "FLO1" | Site ==
                "KPPJT", "On", "Off"
        ),
        .after = Project
        )
print(landscape_appearance_database)
```

To fix the problem we created in the previous step, we will set the value for the "Territory" column to NA if the project is "White Mountains". If the project is "Heber" then we won't change the value for the "Territory".
```{r Set White Mountains "Territory" values to NA}
landscape_appearance_database %>% 
  dplyr::mutate(Territory = if_else(Project == "White Mountains", # logical condition
                                    NA_character_, # true
                                    Territory, # false
                                    ) # nothing for missing values
                )
```


To calculate landscape appearance for Heber 2021, we first need to select just the data from 2021 and from the Heber project. Then we group by site, date, and territory. The "Territory" column will be used to control the plotting order in a future step, and if we don't group by it, it will be dropped by rstatix.

```{r Heber 2021 Landscape Appearance Stats}
heber_2021_stats <- landscape_appearance_database %>% 
  dplyr::filter(Year == 2021) %>%
  dplyr::filter(Project == "Heber") %>%
  dplyr::group_by(Site, Date, Territory) %>% 
  rstatix::get_summary_stats('Class Mid-Point', 
                             type = "common",
                             show = c("n", "mean", "sd", "ci"))
print(heber_2021_stats)
```

Technically, this stats data frame already contains a column called "ci" which contains the confidence interval. However, it can be hard to interpret this number because you have subtract it from the mean to get the lower bounds, and add it to the mean to get the upper bounds. To make interpretation easier, we'll perform those operations and create new columns to hold that information.

```{r Add Confidence Intervals Heber 2021}
heber_2021_stats <- heber_2021_stats  %>% 
  dplyr::mutate(lower_95 = mean - ci) %>% 
  dplyr::mutate(upper_95 = mean + ci)
print(heber_2021_stats)
```

We need to set the "Territory" variable as a factor, primarily because we want to control the order of plotting in ggplot2. If they are in this order, all of the sites that are on territory will be plotted first, and then all of the sites that are off territory will be plotted last.  

First we need to arrange the data frame based on the "Territory" variable. Then we can set "Territory" as a factor.

```{r Arrange by Territory and Set as Factor}
heber_2021_stats <- heber_2021_stats %>% 
  arrange(desc(Territory))

heber_2021_stats$Territory <- heber_2021_stats %>% 
  pull(Territory) %>% 
  as_factor()
print(heber_2021_stats)
```

We need to set the "Site" variable as a factor because ggplot2 treats factors differently than characters. We can plot each factor together if they share the same factor level.

```{r Convert "Site" from Character to Factor Heber 2020}
heber_2021_stats$Site <- heber_2021_stats %>% 
  pull(Site) %>% 
  forcats::as_factor() %>% 
  forcats::fct_inorder()
print(heber_2021_stats)
```

We need to create a new variable called "Monsoon" that we can use to group the two landscape appearance measurements, one which was done in late June, and the other which was done in late November. We can create a cut-off to label each measurement, all measurements before July 1, 2021 are "Pre" monsoon measurements, and any measurements after July 1, 2021 and "Post" monsoon measurements.

We expect utilization to be higher in June because vegetation has not responded to the summer rainfall (as it likely hasn't happened yet), and  animals have been grazing the vegetation since the last growth. 

```{r Add "Monsoon" Column}
heber_2021_stats <- heber_2021_stats %>% 
  dplyr::mutate(Monsoon = if_else(heber_2021_stats$Date < ymd("2021-07-01"), 
                                  "Pre", 
                                  "Post"),
                .after = Date)
print(heber_2021_stats)
```

We need to convert the "Monsoon" column from a character type into a factor type. The package ggplot2 treats factors differently than characters, and factors can be used to plot with as groups, or sub-groups.

```{r Set "Monsoon" as Factor}
heber_2021_stats$Monsoon <- heber_2021_stats %>% 
  pull(Monsoon) %>% 
  forcats::as_factor()
print(heber_2021_stats)
```

```{r}
heber_2021_stats <- heber_2021_stats %>% 
  mutate(Month = as.character(month(Date, label = TRUE, abbr = FALSE)), .after = Monsoon)
print(heber_2021_stats)
```

```{r}
heber_2021_stats$Month <- 
heber_2021_stats %>% 
  pull(Month) %>% 
  forcats::as_factor()
```


```{r}
c("#4472C4", "#ED7D31", "#FFC000")
```

```{r}
show_col(c("#4472C4", "#ED7D31", "#FFC000"))
```


```{r Plot Heber 2021 Landscape Appearance Figure}
heber_2021_stats %>%
  ggplot(aes(fill = Month, x = Site, y = mean)) +
  geom_col(position = "dodge") +
  guides(fill = "legend") +
  labs(title = expression(atop("Heber Wild Horse Territory", 
                               paste("Landscape Appearance")
                               )
                          ),
       subtitle = "2021"
       ) +
  ylab("Average % Utilization ± 95% CI") +
  scale_y_continuous(limits = c(0, 100),
                     breaks = seq(0, 100, by = 10)) +
  scale_fill_manual(breaks = c("June", "November"),
                    values = c("#4472C4", "#FFC000")) + 
  geom_errorbar(aes(ymin = (mean - ci), 
                    ymax = (mean + ci)), 
                position = position_dodge(0.9),
                width = 0.25) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 0, r = 0, b = 10, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 10))) +
  annotate(geom = "text",
           x = 0.75,
           y = (heber_2021_stats$mean[1] + heber_2021_stats$ci[1] + 7),
           label = paste0(signif(heber_2021_stats$mean[1], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 1.2,
           y = (heber_2021_stats$mean[2] + heber_2021_stats$ci[2] + 7),
           label = paste0(signif(heber_2021_stats$mean[2], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 1.75,
           y = (heber_2021_stats$mean[3] + heber_2021_stats$ci[3] + 7),
           label = paste0(signif(heber_2021_stats$mean[3], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 2.2,
           y = (heber_2021_stats$mean[4] + heber_2021_stats$ci[4] + 7),
           label = paste0(signif(heber_2021_stats$mean[4], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 2.75,
           y = (heber_2021_stats$mean[5] + heber_2021_stats$ci[5] + 7),
           label = paste0(signif(heber_2021_stats$mean[5], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 3.2,
           y = (heber_2021_stats$mean[6] + heber_2021_stats$ci[6] + 7),
           label = paste0(signif(heber_2021_stats$mean[6], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 3.75,
           y = (heber_2021_stats$mean[7] + heber_2021_stats$ci[7] + 7),
           label = paste0(signif(heber_2021_stats$mean[7], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 4.2,
           y = (heber_2021_stats$mean[8] + heber_2021_stats$ci[8] + 7),
           label = paste0(signif(heber_2021_stats$mean[8], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 4.75,
           y = (heber_2021_stats$mean[9] + heber_2021_stats$ci[9] + 7),
           label = paste0(signif(heber_2021_stats$mean[9], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 5.2,
           y = (heber_2021_stats$mean[10] + heber_2021_stats$ci[10] + 7),
           label = paste0(signif(heber_2021_stats$mean[10], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 5.75,
           y = (heber_2021_stats$mean[11] + heber_2021_stats$ci[11] + 7),
           label = paste0(signif(heber_2021_stats$mean[11], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 6.2,
           y = (heber_2021_stats$mean[12] + heber_2021_stats$ci[12] + 7),
           label = paste0(signif(heber_2021_stats$mean[12], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 6.75,
           y = (heber_2021_stats$mean[13] + heber_2021_stats$ci[13] + 7),
           label = paste0(signif(heber_2021_stats$mean[13], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 7.2,
           y = (heber_2021_stats$mean[14] + heber_2021_stats$ci[14] + 7),
           label = paste0(signif(heber_2021_stats$mean[14], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 7.75,
           y = (heber_2021_stats$mean[15] + heber_2021_stats$ci[15] + 7),
           label = paste0(signif(heber_2021_stats$mean[15], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 8.2,
           y = (heber_2021_stats$mean[16] + heber_2021_stats$ci[16] + 7),
           label = paste0(signif(heber_2021_stats$mean[16], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 8.75,
           y = (heber_2021_stats$mean[17] + heber_2021_stats$ci[17] + 7),
           label = paste0(signif(heber_2021_stats$mean[17], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 9.2,
           y = (heber_2021_stats$mean[18] + heber_2021_stats$ci[18] + 7),
           label = paste0(signif(heber_2021_stats$mean[18], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 9.75,
           y = (heber_2021_stats$mean[19] + heber_2021_stats$ci[19] + 7),
           label = paste0(signif(heber_2021_stats$mean[19], 2), "%"),
           size = 3,
           angle = 90) +
  annotate(geom = "text",
           x = 10.2,
           y = (heber_2021_stats$mean[20] + heber_2021_stats$ci[20] + 7),
           label = paste0(signif(heber_2021_stats$mean[20], 2), "%"),
           size = 3,
           angle = 90)
ggsave("2021-Heber-Landscape-Appearance-95CI.jpg",
   path = paste0(getwd(),"/figures", "/landscape-appearance"),
   width = 9,
   height = 6,
   units = "in")
```

