---
title: "Landscape Appearance"
author: "Andrew Antaya"
date: "3/9/2022"
output: html_notebook
---

First, let's remove all objects from the environment to start fresh each time.

```{r clear env}
# clear the enviroment
rm(list=ls(all=TRUE))
```

Setup the R environment using a separate script. This helps me stay consistent with environmental variables that I use across multiple R scripts.

```{r setup env}
# the source() function executes all lines of code in the "mentioned" script (i.e. the pathway)
source(paste0(getwd(), "/environment.R"))
print(currentwd)
```

Check that the working directory is correct for your computer.

Then, let's get our R environment ready by loading some useful packages.

```{r load packages, include=FALSE}
# "inlcude=FALSE" in the chunk evaluates the code, but doesn't write the output to the knitr document
# loading packages involves alot of output in the console that we don't need in the knitr document
source(paste0(currentwd, "/packages.R"))
```

This separate R script contains all of the functions that I commonly use across multiple scripts. This chunk of code reads in those functions into the global R environment.

```{r load functions}
source(paste0(currentwd, "/functions.R"))
```


```{r}
BGW_2019_landscape_appearance <- readr::read_csv(
  'data/vegetation/white-mountains/2019-boggy-grazed-landscape-appearance.csv',
  col_names = TRUE, 
  na = c(""," ","NA"))

WCS_2019_landscape_appearance <- readr::read_csv(
  'data/vegetation/white-mountains/2019-wildcat-grazed-landscape-appearance.csv',
  col_names = TRUE, 
  na = c(""," ","NA"))

BGW_2019_landscape_appearance
WCS_2019_landscape_appearance
```
```{r}
BGW_2019_landscape_appearance <- 
  BGW_2019_landscape_appearance %>% 
  mutate(Site = "Boggy", Year = "2019")

WCS_2019_landscape_appearance <- 
  WCS_2019_landscape_appearance %>% 
  mutate(Site = "Wildcat", Year = "2019")

BGW_2019_landscape_appearance <- 
  BGW_2019_landscape_appearance %>% 
  dplyr::select(-c( "Species/Category Name", "Species/Category Code", "Qualifier"))

WCS_2019_landscape_appearance <- 
  WCS_2019_landscape_appearance %>% 
  dplyr::select(-c( "Species/Category Name", "Species/Category Code", "Qualifier"))

BGW_2019_landscape_appearance
WCS_2019_landscape_appearance
```

```{r Read in Excel data and convert to csv, eval=FALSE, include=FALSE}
# this code chunk only needs to be turned on once when converting data
# then it can be turned off after the files are converted

# list all of the xlsx data files in the directory
xlsx_file_list <- list.files("data/vegetation/heber/landscape-appearance/xlsx", pattern = "xlsx")

# create a vector of file names that we will use to rename our xlsx files into csv files
# do this by replacing the file extension but otherwise keep the file name the same
file_names <- str_replace_all(xlsx_file_list, "xlsx", "csv")

# create a vector of file paths to tell R where to find the source xlsx data
file_source <- paste0(getwd(), "/data/vegetation/heber/landscape-appearance/xlsx/", xlsx_file_list)

# create a vector of file paths to tell R where to put the files after conversion
file_destination <- paste0(getwd(), "/data/vegetation/heber/landscape-appearance/csv/", file_names)

# for loop through the file list to convert all xlsx files in the directory
# to csv files
for (i in 1:length(file_source)) {
  # read the data from the Stubble Height sheet
  xlsx_data <- openxlsx::read.xlsx(file_source[i], sheet = "Ocular Estimates")
  # write out the xlsm data as an xlsx
  readr::write_csv(xlsx_data, paste0(file_destination[i]), na = "NA")}
```

```{r}
heber_file_list <- list.files("data/vegetation/heber/landscape-appearance/csv", pattern = "csv")

heber_file_list
```

```{r load data}
BKS_2018_landscape_data <-
  readr::read_csv(
    paste0(
      getwd(),
      "/data/vegetation/heber/landscape-appearance/csv/",
      "2018-BKS-landscape-appearance.csv"),
      col_names = TRUE,
      na = c("", " ", "NA")
    )

BRL_2018_landscape_data <-
  readr::read_csv(
    paste0(
      getwd(),
      "/data/vegetation/heber/landscape-appearance/csv/",
      "2018-BRL-landscape-appearance.csv"),
      col_names = TRUE,
      na = c("", " ", "NA")
    )

A51_2019_landscape_data <- readr::read_csv(
  paste0(
    getwd(),
    "/data/vegetation/heber/landscape-appearance/csv/",
    "2019-A51-landscape-appearance.csv"),
    col_names = TRUE,
    na = c("", " ", "NA")
  )

BKN_2019_landscape_data <- readr::read_csv(
  paste0(
    getwd(),
    "/data/vegetation/heber/landscape-appearance/csv/",
    "2019-BKN-landscape-appearance.csv"
  )
)
BRL_2019_landscape_data <- readr::read_csv(
  paste0(
    getwd(),
    "/data/vegetation/heber/landscape-appearance/csv/",
    "2019-BRL-landscape-appearance.csv"
  )
)
A51_2020_landscape_data <- readr::read_csv(
  paste0(
    getwd(),
    "/data/vegetation/heber/landscape-appearance/csv/",
    "2020-A51-landscape-appearance.csv"
  )
)

BKN_2020_landscape_data <- readr::read_csv(
  paste0(
    getwd(),
    "/data/vegetation/heber/landscape-appearance/csv/",
    "2020-BKN-landscape-appearance.csv"
  )
)

BKS_2020_landscape_data <- readr::read_csv(
  paste0(
    getwd(),
    "/data/vegetation/heber/landscape-appearance/csv/",
    "2020-BKS-landscape-appearance.csv"
  )
)

BRL_2020_landscape_data <- readr::read_csv(
  paste0(
    getwd(),
    "/data/vegetation/heber/landscape-appearance/csv/",
    "2020-BRL-landscape-appearance.csv"
  )
)

```

```{r view data}
BKS_2018_landscape_data
BRL_2018_landscape_data
A51_2019_landscape_data
BKN_2019_landscape_data
BRL_2019_landscape_data
A51_2020_landscape_data
BKN_2020_landscape_data
BKS_2020_landscape_data
BRL_2020_landscape_data
```

The 2018 data is in a different format than 2019 or 2020 data. 
```{r}

```


```{r}
BKS_2018_landscape_data <-
  BKS_2018_landscape_data %>% mutate(Site = "BKS", Year = "2018")

BRL_2018_landscape_data <-
  BKS_2018_landscape_data %>% mutate(Site = "BRL", Year = "2018")

A51_2019_landscape_data <-
  A51_2019_landscape_data %>% mutate(Site = "A51", Year = "2019")

BKN_2019_landscape_data <-
  BKN_2019_landscape_data %>% mutate(Site = "BKN", Year = "2019")

BRL_2019_landscape_data <-
  BRL_2019_landscape_data %>% mutate(Site = "BRL", Year = "2019")

A51_2020_landscape_data <-
  A51_2020_landscape_data %>% mutate(Site = "A51", Year = "2020")

BKN_2020_landscape_data <-
  BKN_2020_landscape_data %>% mutate(Site = "BKN", Year = "2020")

BKS_2020_landscape_data <-
  BKS_2020_landscape_data %>% mutate(Site = "BKS", Year = "2020")

BRL_2020_landscape_data <-
  BRL_2020_landscape_data %>% mutate(Site = "BRL", Year = "2020")

heber_2019_landscape_appearance <- dplyr::bind_rows(A51_2019_landscape_data, 
                                                    BKN_2019_landscape_data,
                                                    BRL_2019_landscape_data)

heber_2020_landscape_appearance <- dplyr::bind_rows(A51_2020_landscape_data,
                                                    BKN_2020_landscape_data,
                                                    BKS_2020_landscape_data,
                                                    BRL_2020_landscape_data)
```

```{r}
heber_2019_landscape_appearance <-
  heber_2019_landscape_appearance %>% dplyr::rename("Class Mid-Point" = "%.Estimate")

heber_2019_landscape_appearance <-
  heber_2019_landscape_appearance %>% dplyr::relocate(c("Site", "Year"), .before = "Transect")

heber_2019_landscape_appearance
```
```{r}
heber_2020_landscape_appearance <-
  heber_2020_landscape_appearance %>% dplyr::rename("Class Mid-Point" = "%.Estimate")

heber_2020_landscape_appearance <-
  heber_2020_landscape_appearance %>% dplyr::relocate(c("Site", "Year"), .before = "Transect")

heber_2020_landscape_appearance
```

```{r}
# heber_2019_landscape_appearance$`Class Mid-Point`<- as.character(heber_2019_landscape_appearance$`Class Mid-Point`)
# 
# heber_2019_landscape_appearance
```


```{r}
heber_2019_landscape_appearance$'Class Mid-Point' <- 
  heber_2019_landscape_appearance %>% pull(`Class Mid-Point`) %>% str_replace_all("90", "88")

heber_2019_landscape_appearance$'Class Mid-Point' <- heber_2019_landscape_appearance %>% 
  pull(`Class Mid-Point`) %>% 
  as.numeric()

heber_2019_landscape_appearance
```


```{r}
heber_2019_landscape_appearance <-
  heber_2019_landscape_appearance %>%
  mutate(Factor = forcats::as_factor(heber_2019_landscape_appearance$`Class Mid-Point`))

heber_2019_landscape_appearance
```

```{r}
levels(heber_2019_landscape_appearance %>% pull(Factor))
```

```{r}
heber_2019_landscape_appearance$Factor <- heber_2019_landscape_appearance %>% 
  pull("Factor") %>% 
  fct_expand("97.5")

levels(heber_2019_landscape_appearance %>% pull("Factor"))
```

```{r}
# heber_2019_landscape_appearance$Factor <- heber_2019_landscape_appearance %>% 
#   pull("Factor") %>% 
#   fct_relabel(~ gsub("90", "88", .x))
# 
# levels(heber_2019_landscape_appearance %>% pull("Factor"))
```

```{r}
BGW_2019_stats <- BGW_2019_landscape_appearance %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")

WCS_2019_stats <- WCS_2019_landscape_appearance %>%
  rstatix::get_summary_stats('Class Mid-Point', type = "common")

BGW_2019_stats <- BGW_2019_stats %>% add_column(Site = "Boggy Creek", .before = "variable")

WCS_2019_stats <- WCS_2019_stats %>% add_column(Site = "Wildcat Creek", .before = "variable")

BGW_2019_stats

WCS_2019_stats
```
```{r}
white_mountains_2019_stats <- dplyr::bind_rows(BGW_2019_stats, WCS_2019_stats)

white_mountains_2019_stats
```

```{r}
A51_2019_stats <- heber_2019_landscape_appearance %>% 
  dplyr::filter(Site == "A51")  %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")

BKN_2019_stats <- heber_2019_landscape_appearance %>% 
  dplyr::filter(Site == "BKN")  %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")

BRL_2019_stats <- heber_2019_landscape_appearance %>% 
  dplyr::filter(Site == "BRL")  %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")

A51_2019_stats
BKN_2019_stats
BRL_2019_stats
```

```{r}
A51_2020_stats <- heber_2020_landscape_appearance %>% 
  dplyr::filter(Site == "A51")  %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")

BKN_2020_stats <- heber_2020_landscape_appearance %>% 
  dplyr::filter(Site == "BKN")  %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")

BRL_2020_stats <- heber_2020_landscape_appearance %>% 
  dplyr::filter(Site == "BRL")  %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")

BKS_2020_stats <- heber_2020_landscape_appearance %>% 
  dplyr::filter(Site == "BKS")  %>% 
  rstatix::get_summary_stats('Class Mid-Point', type = "common")
                             
A51_2020_stats
BKN_2020_stats
BRL_2020_stats
BKS_2020_stats
```

```{r}
A51_2019_stats <- A51_2019_stats %>% add_column(Site = "Fifty One", .before = "variable")

BKN_2019_stats <- BKN_2019_stats %>% add_column(Site = "Black Canyon North", .before = "variable")

BRL_2019_stats <- BRL_2019_stats %>% add_column(Site = "Bear", .before = "variable")

A51_2019_stats
BKN_2019_stats
BRL_2019_stats
```
```{r}
A51_2020_stats <- A51_2020_stats %>% add_column(Site = "Fifty One", .before = "variable")

BKN_2020_stats <- BKN_2020_stats %>% add_column(Site = "Black Canyon North", .before = "variable")

BRL_2020_stats <- BRL_2020_stats %>% add_column(Site = "Bear", .before = "variable")

BKS_2020_stats <- BKS_2020_stats %>% add_column(Site = "Black Canyon South", .before = "variable")

A51_2020_stats
BKN_2020_stats
BRL_2020_stats
BKS_2020_stats
```

```{r}
heber_2019_stats <- bind_rows(BRL_2019_stats, BKN_2019_stats, A51_2019_stats)

heber_2019_stats
```

```{r}
heber_2019_stats$Site <- heber_2019_stats %>% pull(Site) %>% forcats::as_factor()

heber_2019_stats$Site <- heber_2019_stats %>% pull(Site) %>% forcats::fct_inorder()

heber_2019_stats
```

```{r}
heber_2020_stats <- bind_rows(BRL_2020_stats, BKN_2020_stats, BKS_2020_stats, A51_2020_stats)

heber_2020_stats
```

```{r}
heber_2020_stats$Site <- heber_2020_stats %>% pull(Site) %>% forcats::as_factor()

heber_2020_stats$Site <- heber_2020_stats %>% pull(Site) %>% forcats::fct_inorder()

heber_2020_stats
```

```{r}
# A51_2019 <- heber_2019_landscape_appearance %>%
#   dplyr::filter(Site == "A51") %>% 
#   pull('Class Mid-Point') %>% 
#   table() %>% 
#   as.data.frame()
# 
# A51_2019
```

```{r}
# heber_2020_landscape_appearance <-
#   heber_2020_landscape_appearance %>% dplyr::rename("Class Mid-Point" = "%.Estimate")

heber_2020_landscape_appearance <-
  heber_2020_landscape_appearance %>% dplyr::relocate(c("Site", "Year"), .before = "Transect")

heber_2020_landscape_appearance$`Class Mid-Point` <-
  heber_2020_landscape_appearance %>%
  pull('Class Mid-Point') %>%
  forcats::as_factor()

heber_2020_landscape_appearance
```

```{r}
levels(heber_2020_landscape_appearance %>% pull("Class Mid-Point"))
```

```{r}
A51_2019_class_midpoints <- 
  heber_2019_landscape_appearance %>% 
  dplyr::filter(Site == "A51") %>% 
  pull(`Factor`) %>%
  forcats::fct_count()

BKN_2019_class_midpoints <-
  heber_2019_landscape_appearance %>%
  dplyr::filter(Site == "BKN") %>%
  pull(`Factor`) %>%
  forcats::fct_count()

BRL_2019_class_midpoints <-
  heber_2019_landscape_appearance %>%
  dplyr::filter(Site == "BRL") %>%
  pull(`Factor`) %>%
  forcats::fct_count()

A51_2019_class_midpoints
BKN_2019_class_midpoints
BRL_2019_class_midpoints
```

```{r}
A51_2019_class_midpoints <- A51_2019_class_midpoints %>% mutate(midpoint = as.character(f))

A51_2019_class_midpoints$midpoint <- as.numeric(A51_2019_class_midpoints$midpoint)

BKN_2019_class_midpoints <- BKN_2019_class_midpoints %>% mutate(midpoint = as.character(f))

BKN_2019_class_midpoints$midpoint <- as.numeric(BKN_2019_class_midpoints$midpoint)

BRL_2019_class_midpoints <- BRL_2019_class_midpoints %>% mutate(midpoint = as.character(f))

BRL_2019_class_midpoints$midpoint <- as.numeric(BRL_2019_class_midpoints$midpoint)

A51_2019_class_midpoints
BKN_2019_class_midpoints
BRL_2019_class_midpoints
```

```{r}
A51_2019_class_midpoints <- A51_2019_class_midpoints %>% mutate(product = midpoint * n)

BKN_2019_class_midpoints <- BKN_2019_class_midpoints %>% mutate(product = midpoint * n)

BRL_2019_class_midpoints <- BRL_2019_class_midpoints %>% mutate(product = midpoint * n)

A51_2019_class_midpoints
BKN_2019_class_midpoints
BRL_2019_class_midpoints
```

```{r}
A51_2019_sum <- sum(A51_2019_class_midpoints$product)

BKN_2019_sum <- sum(BKN_2019_class_midpoints$product)

BRL_2019_sum <- sum(BRL_2019_class_midpoints$product)

A51_2019_sum
BKN_2019_sum
BRL_2019_sum
```

```{r}
A51_2019_num_observations <- A51_2019_class_midpoints %>% pull('n') %>% sum()

BKN_2019_num_observations<- BKN_2019_class_midpoints %>% pull('n') %>% sum()

BRL_2019_num_observations <- BRL_2019_class_midpoints %>% pull('n') %>% sum()

A51_2019_num_observations

BKN_2019_num_observations

BRL_2019_num_observations
```

```{r}
A51_2019_sum / A51_2019_num_observations

BKN_2019_sum / BKN_2019_num_observations

BRL_2019_sum / BRL_2019_num_observations
```

```{r}
A51_2020_class_midpoints <- 
  heber_2020_landscape_appearance %>% 
  dplyr::filter(Site == "A51" & Year == 2020) %>% 
  pull(`Class Mid-Point`) %>% 
  forcats::fct_count()

BKN_2020_class_midpoints <- 
  heber_2020_landscape_appearance %>% 
  dplyr::filter(Site == "BKN" & Year == 2020) %>% 
  pull(`Class Mid-Point`) %>% 
  forcats::fct_count()

BKS_2020_class_midpoints <- 
  heber_2020_landscape_appearance %>% 
  dplyr::filter(Site == "BKS" & Year == 2020) %>% 
  pull(`Class Mid-Point`) %>% 
  forcats::fct_count()

BRL_2020_class_midpoints <- 
  heber_2020_landscape_appearance %>% 
  dplyr::filter(Site == "BRL" & Year == 2020) %>% 
  pull(`Class Mid-Point`) %>% 
  forcats::fct_count()

A51_2020_class_midpoints
BKN_2020_class_midpoints
BKS_2020_class_midpoints
BRL_2020_class_midpoints
```

```{r}
ggplot(white_mountains_2019_stats, aes(fill = Site, x = Site, y = mean)) +
  geom_col(width = 0.75) +
  guides(fill = "none") +
  labs(title = "White Mountains Landscape Appearance 2019") +
  ylab(expression(atop("Average % Utilization ± 95% CI", paste("(lower is better)")))) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
  geom_errorbar(aes(ymin = (mean-ci), ymax = (mean+ci)), position = position_dodge(0.5), width = 0.25) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 0, r = 0, b = 10, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 10))) +
  # add % utilization values above the  error bars
  # round the mean value using significant figures
  annotate(geom = "text", 
           x = 1, 
           y = (white_mountains_2019_stats$mean[1] + white_mountains_2019_stats$ci[1] + 7), 
           label = paste0(signif(white_mountains_2019_stats$mean[1], 2), "%")) +
  annotate(geom = "text", 
           x = 2, 
           y = (white_mountains_2019_stats$mean[2] + white_mountains_2019_stats$ci[2] + 7), 
           label = paste0(signif(white_mountains_2019_stats$mean[2], 2), "%"))

# ggsave("2019-White-Mountains-Landscape-Appearance-95CI.jpg",
#    path = paste0(getwd(),"/figures", "/landscape-appearance"))
```

```{r plot heber landscape appearance 2019}
ggplot(heber_2019_stats, aes(fill = Site, x = Site, y = mean)) +
  geom_col(width = 0.75) +
  guides(fill = "none") +
  labs(title = "Heber Landscape Appearance 2019") +
  ylab(expression(atop("Average % Utilization ± 95% CI", paste("(lower is better)")))) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
  geom_errorbar(aes(ymin = (mean-ci), ymax = (mean+ci)), position = position_dodge(0.5), width = 0.25) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 0, r = 0, b = 10, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 10))) +
  # add % utilization values above the  error bars
  # round the mean value using significant figures
  annotate(geom = "text", 
           x = 1, 
           y = (heber_2019_stats$mean[1] + heber_2019_stats$ci[1] + 7), 
           label = paste0(signif(heber_2019_stats$mean[1], 2), "%")) +
  annotate(geom = "text", 
           x = 2, 
           y = (heber_2019_stats$mean[2] + heber_2019_stats$ci[2] + 7), 
           label = paste0(signif(heber_2019_stats$mean[2], 2), "%")) +
  annotate(geom = "text", 
           x = 3, 
           y = (heber_2019_stats$mean[3] + heber_2019_stats$ci[3] + 7), 
           label = paste0(signif(heber_2019_stats$mean[3], 2), "%"))

# ggsave("2019-Heber-Landscape-Appearance-95CI.jpg", 
#     path = paste0(getwd(),"/figures", "/landscape-appearance"))
```

```{r plot heber landscape appearance 2020}
ggplot(heber_2020_stats, aes(fill = Site, x = Site, y = mean)) +
  geom_col(width = 0.75) +
  guides(fill = "none") +
  labs(title = "Heber Landscape Appearance 2020") +
  ylab(expression(atop("Average % Utilization ± 95% CI", paste("(lower is better)")))) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
  geom_errorbar(aes(ymin = (mean-ci), ymax = (mean+ci)), position = position_dodge(0.5), width = 0.25) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 0, r = 0, b = 10, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 10))) +
  # add % utilization values above the  error bars
  # round the mean value using significant figures
  annotate(geom = "text", 
           x = 1, 
           y = (heber_2020_stats$mean[1] + heber_2020_stats$ci[1] + 7), 
           label = paste0(signif(heber_2020_stats$mean[1], 2), "%")) +
  annotate(geom = "text", 
           x = 2, 
           y = (heber_2020_stats$mean[2] + heber_2020_stats$ci[2] + 7), 
           label = paste0(signif(heber_2020_stats$mean[2], 2), "%")) +
  annotate(geom = "text", 
           x = 3, 
           y = (heber_2020_stats$mean[3] + heber_2020_stats$ci[3] + 7), 
           label = paste0(signif(heber_2020_stats$mean[3], 2), "%")) +
    annotate(geom = "text", 
           x = 4, 
           y = (heber_2020_stats$mean[4] + heber_2020_stats$ci[4] + 7), 
           label = paste0(signif(heber_2020_stats$mean[4], 2), "%"))
# ggsave("2020-Heber-Landscape-Appearance-95CI.jpg", 
#     path = paste0(getwd(),"/figures", "/landscape-appearance"))
```