---
title: "Photo Data Pre-Processing- White Mountains, Arizona"
output: html_notebook
author: "Andrew Antaya"
---
***
First, let's get our R environment ready by loading some useful packages.
```{r}
# load packages and dependencies
library("ggplot2", lib.loc= "~/R/win-library/3.5")
library("dplyr", lib.loc= "~/R/win-library/3.5")
library("jpeg", lib.loc= "~/R/win-library/3.5")
library("viridis", lib.loc = "~/R/win-library/3.5")
library("scales", lib.loc = "~/R/win-library/3.5")
```
***

Then, let's remove all objects from the environment to start fresh each time.
```{r}
# clear the enviroment
rm(list=ls(all=TRUE))
```

***
Let's check the working directory to see if it's correct.
```{r}
# check working directory
getwd()
```
Looks good for my (Andrew's) PC

***
Let's read in the RAW photo data from 2017 and 2018, which human observers classified in a custom Excel macro (written in VBA). These RAW photo data files have a file extension of .xlsm. We then saved the .xlsm files as .csv files for ease of use in R and to convert to a non-proprietary format.
```{r}
## read in the 2018 data, treating all blanks, spaces, and "NA"s as NA's
BGX18RAW<-read.csv('data/photo/BGX_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
BGW18RAW<-read.csv('data/photo/BGW_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
BGT18RAW<-read.csv('data/photo/BGT_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
WCX18RAW<-read.csv('data/photo/WCX_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
WCS18RAW<-read.csv('data/photo/WCS_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
WCT18RAW<-read.csv('data/photo/WCT_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
```
For the first step in cleaing up the data, we are going to treat all fields with "NA" (characters), "" (blanks), or " " (spaces- typically accidental input which is invisble in Excel) as NAs inside R. This will help us deal with missing information in our dataset.

***
