---
title: "R Notebook"
output: html_notebook
---
White Mountain Sites
Boggy and Wildcat Creek Grazed Sites
Production and Utilization calculations
02/07/2019
Written by Andrew Antaya

```{r echo=False}
# clear the enviroment
rm(list=ls(all=TRUE))
```

```{r echo=FALSE}
source("packages.R")
```

```{r}
source("functions.R")
```

Read in the vegetation data from the White Mountains study sites.
```{r}
## read in data
wm_prod_2017 <- readr::read_csv('data/vegetation/white-mountains/2017-white-mountains-production-reordered.csv',
                                col_names = TRUE, 
                                na = c(""," ","NA"))

wm_prod_2018 <- readr::read_csv('data/vegetation/white-mountains/2018-white-mountains-production-reordered.csv',
                                col_names = TRUE,
                                na = c(""," ","NA"))

wm_prod_2019 <- readr::read_csv('data/vegetation/white-mountains/2019-white-mountains-production.csv',
                                col_names = TRUE,
                                na = c(""," ","NA"))

```
The output of readr::read_csv shows our column names, and how they're stored inside R.
For example, the "Plot" column is recognized as a character column in 2017 and 2018, but as a double column in 2019.

Printing the data frames lets us take a look at 
```{r}
print(wm_prod_2017)

print(wm_prod_2018)

print(wm_prod_2019)
```


```{r}
# remove the first column
prod1718$Record <- NULL
# rename the ID column to "Cage" to match the 2019 data
prod1718 <- prod1718 %>% rename(Plot = ID)
# reorder the 2017-2018 data to align with the 2019 data
prod1718<- prod1718[ , c("Site", "Type", "Year", "Plot", "Bag1DryWt", "Bag2DryWt", "Bag3DryWt", "Bag4DryWt", "Bag5DryWt", "Bag6DryWt", "Bag7DryWt", "Bag8DryWt", "TotalDry")]

prod19$Bag6DryWt <- NA
prod19$Bag7DryWt <- NA
prod19$Bag8DryWt <- NA

prod19<- prod19[ , c("Site", "Type", "Year", "Plot", "Bag1DryWt", "Bag2DryWt", "Bag3DryWt", "Bag4DryWt", "Bag5DryWt", "Bag6DryWt", "Bag7DryWt", "Bag8DryWt", "TotalDry")]

prod1718[prod1718 == 0] <- NA
prod19[prod19 == 0] <- NA

prod19$Plot <- as.factor(prod19$Plot)

# view the data frames
prod1718
prod19
```

```{r}
dim_x = set_units(40, cm) # length of dimension X in centimeters
dim_y = set_units(40, cm) # length of dimension Y in centimeters
n = 3                     # number of quadrats

area = dim_x*dim_y
area

totalarea = area*n
totalarea

area_m2 = set_units(totalarea, m^2)
area_m2

conversion = as.numeric(1/area_m2)

prod19$TotalDry <- ifelse (prod19$Site == "Wildcat" & prod19$Type == "Exclosure", prod19$TotalDry*conversion, prod19$TotalDry)

prod19

#write.csv(prod19, 'data/vegetation/White-Mountain-Production-2019-Wildcat-Adjusted.csv', row.names = FALSE)
```

```{r}
prod17 <- filter(prod1718, Year == 2017)

prod17 <- arrange(prod17, Type)

prod17
#write.csv(prod17, 'data/vegetation/White-Mountain-Production-2017-Reordered.csv', row.names = FALSE)
```

```{r}
prod18 <- filter(prod1718, Year == 2018)

prod18 <- arrange(prod18, Type)

prod18

#write.csv(prod18, 'data/vegetation/White-Mountain-Production-2018-Reordered.csv', row.names = FALSE)
```

```{r}
#rm(prod1718)
```

```{r}
prod <- rbind(prod17, prod18, prod19)

resd <- filter(prod, Type == "Residual")

prod <- filter(prod, Type == "Exclosure")

#View(prod)
#View(resd)
```

```{r}
prod$TotalDry <- set_units(prod$TotalDry, g/m^2)
prod$kg_ha <- NA
prod$kg_ha <- set_units(prod$TotalDry, kg/hectare)
prod$lb_acre <- NA
prod$lb_acre <- set_units(prod$TotalDry, lb/acre)
prod
```

Create empty data frame to store the mean, standard deviation, standard error, 95% confidence interval for all sites.
```{r}
stats<- data.frame(sites=c("BGW17", "BGW18", "BGW19", "WCS17", "WCS18", "WCS19"), avg_grams_meter = NA, avg_kg_hectare = NA, avg_lbs_acre = NA, sd = NA, se = NA, L95 = NA, U95 = NA)
stats
```

```{r}
## calculate mean production values for each year and site (in g/m2)
stats$avg_grams_meter[1] <- mean(pull(filter(prod, Site == "Boggy" & Year == "2017"), "TotalDry"))
stats$avg_grams_meter[2] <- mean(pull(filter(prod, Site == "Boggy" & Year == "2018"), "TotalDry"))
stats$avg_grams_meter[3] <- mean(pull(filter(prod, Site == "Boggy" & Year == "2019"), "TotalDry"))
stats$avg_grams_meter[4] <- mean(pull(filter(prod, Site == "Wildcat" & Year == "2017"), "TotalDry"))
stats$avg_grams_meter[5] <- mean(pull(filter(prod, Site == "Wildcat" & Year == "2018"), "TotalDry"))
stats$avg_grams_meter[6] <- mean(pull(filter(prod, Site == "Wildcat" & Year == "2019"), "TotalDry"))
stats
```

```{r}
# Convert to different units using the set_units() function
stats$avg_grams_meter <- set_units(stats$avg_grams_meter, g/m^2)
stats$avg_kg_hectare <- set_units(stats$avg_grams_meter, kg/hectare)
stats$avg_lbs_acre <- set_units(stats$avg_grams_meter, lb/acre)
stats$avg_grams_meter <- as.numeric(stats$avg_grams_meter)
stats$avg_kg_hectare <- as.numeric(stats$avg_kg_hectare)
stats$avg_lbs_acre <- as.numeric(stats$avg_lbs_acre)
stats
```
```{r}
testavg <- mean(pull(filter(prod, Site == "Boggy" & Year == "2017"), "lb_acre"))
testavg

testsd <- sd(pull(filter(prod, Site == "Boggy" & Year == "2017"), "lb_acre"))
testsd

testse <- se(pull(filter(prod, Site == "Boggy" & Year == "2017"), "lb_acre"))
testse
```

```{r}
## calculate standard deviation SD for each year and site (in g/m2)
stats$sd[1] <- sd(pull(filter(prod, Site == "Boggy" & Year == "2017"), "lb_acre"))
stats$sd[2] <- sd(pull(filter(prod, Site == "Boggy" & Year == "2018"), "lb_acre"))
stats$sd[3] <- sd(pull(filter(prod, Site == "Boggy" & Year == "2019"), "lb_acre"))
stats$sd[4] <- sd(pull(filter(prod, Site == "Wildcat" & Year == "2017"), "lb_acre"))
stats$sd[5] <- sd(pull(filter(prod, Site == "Wildcat" & Year == "2018"), "lb_acre"))
stats$sd[6] <- sd(pull(filter(prod, Site == "Wildcat" & Year == "2019"), "lb_acre"))
stats
```

```{r}
## calculate standard deviation SD for each year and site (in g/m2)
stats$se[1] <- se(pull(filter(prod, Site == "Boggy" & Year == "2017"), "lb_acre"))
stats$se[2] <- se(pull(filter(prod, Site == "Boggy" & Year == "2018"), "lb_acre"))
stats$se[3] <- se(pull(filter(prod, Site == "Boggy" & Year == "2019"), "lb_acre"))
stats$se[4] <- se(pull(filter(prod, Site == "Wildcat" & Year == "2017"), "lb_acre"))
stats$se[5] <- se(pull(filter(prod, Site == "Wildcat" & Year == "2018"), "lb_acre"))
stats$se[6] <- se(pull(filter(prod, Site == "Wildcat" & Year == "2019"), "lb_acre"))
stats
```
```{r}
## calculate standard deviation SD for each year and site (in g/m2)
stats$se[1] <- se(pull(filter(prod, Site == "Boggy" & Year == "2017"), "lb_acre"))
stats$se[2] <- se(pull(filter(prod, Site == "Boggy" & Year == "2018"), "lb_acre"))
stats$se[3] <- se(pull(filter(prod, Site == "Boggy" & Year == "2019"), "lb_acre"))
stats$se[4] <- se(pull(filter(prod, Site == "Wildcat" & Year == "2017"), "lb_acre"))
stats$se[5] <- se(pull(filter(prod, Site == "Wildcat" & Year == "2018"), "lb_acre"))
stats$se[6] <- se(pull(filter(prod, Site == "Wildcat" & Year == "2019"), "lb_acre"))
stats
```

 <- 8.92179*(mean(BGW17E$TotalDry)-2.571*se(BGW17E$TotalDry))
```{r}
stats$L95 <- stats$avg_lbs_acre-2.571*stats$se
stats$U95 <- stats$avg_lbs_acre+2.571*stats$se
stats
```

```{r}
jpeg(filename = "figures/test/Production.jpeg",
    width=6.5,
    height=6.5,
    units="in",
    res=300)
plot.new()
# bottom, left, top, right
par(mar=c(5, 5, 5, 2))
barplot(as.numeric(stats$avg_lbs_acre),
        col = c(rep("red", 3), rep("blue", 3)),
        axes = FALSE,
        #names.arg=(c("Production", "Availability")),
        ylab = expression(paste("pounds ", "acre"^"-1", " ± SE")),
        cex.lab = 1,
        cex.main = 1,
        ylim = c(0, 6500))
title(main = "White Mountain Vegetation Production")
mtext("2017-2019", 3, adj = 0.5)

axis(2, at=c(seq(0,6500,1000)),labels=c(seq(0,6500,1000)), cex.axis= 0.75, las = 2)
axis(1, at=c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7), labels = c("Boggy 2017", "Boggy 2018", "Boggy 2019", "Wildcat 2017", "Wildcat 2018", "Wildcat 2019"), cex.axis= 0.75, las = 2)

segments(0.7, stats$avg_lbs_acre[1] - stats$se[1], 0.7, stats$avg_lbs_acre[1] + stats$se[1], lwd = 1)
arrows(0.7, stats$avg_lbs_acre[1]-stats$se[1], 0.7, stats$avg_lbs_acre[1] + stats$se[1], lwd = 1, angle = 90, code = 3, length = 0.05)

segments(1.9, stats$avg_lbs_acre[2] - stats$se[2], 1.9, stats$avg_lbs_acre[2] + stats$se[2], lwd = 1)
arrows(1.9, stats$avg_lbs_acre[2] - stats$se[2], 1.9, stats$avg_lbs_acre[2] + stats$se[2], lwd = 1, angle = 90,code = 3, length = 0.05)

segments(3.1, stats$avg_lbs_acre[3] - stats$se[3], 3.1, stats$avg_lbs_acre[3] + stats$se[3], lwd = 1)
arrows(3.1, stats$avg_lbs_acre[3] - stats$se[3], 3.1, stats$avg_lbs_acre[3] + stats$se[3], lwd = 1, angle = 90,code = 3, length = 0.05)

segments(4.3, stats$avg_lbs_acre[4] - stats$se[4], 4.3, stats$avg_lbs_acre[4] + stats$se[4], lwd = 1)
arrows(4.3, stats$avg_lbs_acre[4] - stats$se[4], 4.3, stats$avg_lbs_acre[4] + stats$se[4], lwd = 1, angle = 90,code = 3, length = 0.05)

segments(5.5, stats$avg_lbs_acre[5] - stats$se[5], 5.5, stats$avg_lbs_acre[5] + stats$se[5], lwd = 1)
arrows(5.5, stats$avg_lbs_acre[5] - stats$se[5], 5.5, stats$avg_lbs_acre[5] + stats$se[5], lwd = 1, angle = 90,code = 3, length = 0.05)

segments(6.7, stats$avg_lbs_acre[6] - stats$se[6], 6.7, stats$avg_lbs_acre[6] + stats$se[6], lwd = 1)
arrows(6.7, stats$avg_lbs_acre[6] - stats$se[6], 6.7, stats$avg_lbs_acre[6] + stats$se[6], lwd = 1, angle = 90,code = 3, length = 0.05)

text(0.7, 5700, "4705", pos = 3, cex = 0.75)
text(1.9, 4200, "3483", pos = 3, cex = 0.75)
text(3.1, 3800, "3035", pos = 3, cex = 0.75)
text(4.3, 5500, "4766", pos = 3, cex = 0.75)
text(5.5, 3900, "3271", pos = 3, cex = 0.75)
text(6.7, 5400, "4813", pos = 3, cex = 0.75)

dev.off()
```