---
title: "Photo Data Pre-Processing- White Mountains, Arizona"
output: html_notebook
author: "Andrew Antaya"
---
***
First, let's get our R environment ready by loading some useful packages.
```{r}
# load packages and dependencies
library("ggplot2", lib.loc= "~/R/win-library/3.5")
library("dplyr", lib.loc= "~/R/win-library/3.5")
library("jpeg", lib.loc= "~/R/win-library/3.5")
library("viridis", lib.loc = "~/R/win-library/3.5")
library("scales", lib.loc = "~/R/win-library/3.5")
```
***
Then, let's remove all objects from the environment to start fresh each time.
```{r}
# clear the enviroment
rm(list=ls(all=TRUE))
```

***
Let's check the working directory to see if it's correct.
```{r}
# check working directory
getwd()
```
Looks good for my (Andrew's) PC 

***
Let's read in the RAW photo data from 2017 and 2018, which human observers classified in a custom Excel macro (written in VBA) which have a file extension of .xlsm. We then saved the .xlsm files as a .csv file for ease of use in a non-proprietary format.
```{r}
## read in the 2018 data, treating all blanks, spaces, and "NA"s as NA's
BGX18RAW<-read.csv('./Data/Photo/BGX_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
BGW18RAW<-read.csv('./Data/Photo/BGW_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
BGT18RAW<-read.csv('./Data/Photo/BGT_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
WCX18RAW<-read.csv('./Data/Photo/WCX_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
WCS18RAW<-read.csv('./Data/Photo/WCS_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
WCT18RAW<-read.csv('./Data/Photo/WCT_Analysis_2018.csv', header=TRUE, na.strings=c(""," ","NA"))
```
For the first step in cleaing up the data, we are going to remove all fields with "NA" (Not Applicable), "" (Blanks), or " " (Spaces- typically accidental input which is invisble in Excel)
***
