---
title: "2021-heber-landscape-appearance-preprocessing"
author: "Andrew Antaya"
date: "4/16/2022"
output:
  html_document: 
    theme: readable
    toc: yes
    toc_depth: 5
    fig_caption: yes
  word_document:
    toc: yes
---

# TODO move this script to the processing folder

# Setup

```{r knitr setup, include=FALSE}
knitr::opts_knit$set(root.dir = currentwd)
```

First, let's remove all objects from the environment to start fresh each time.

```{r clear environment, eval=FALSE}
# rm(list = ls(all = TRUE))
```

```{r setup environment}
source(file.path("", "home", "rstudio", "grazing-interaction", "environment.R"))
```

# TODO figure out why the X1 column doens't exist in the 2021-heber-landscape-appearance-vgs.csv file

# Load Data

```{r Load 2021 Heber Landscape Appearance Data}
heber_2021_landscape_appearance <- readr::read_csv(
    file.path(currentwd,
              "data",
              "landscape-appearance",
              "heber",
              "2021-heber-landscape-appearance-vgs.csv"
    ),
    col_names = TRUE, na = c("", " ", "NA")
)

print(heber_2021_landscape_appearance)
```

# Clean Data

## Remove Unnecessary Columns

```{r}
heber_2021_landscape_appearance <- heber_2021_landscape_appearance %>% 
  dplyr::select(-c("ProtocolType", 
                   "FormName", 
                   "Element"))
print(heber_2021_landscape_appearance)
```

## Rename Columns

Some of the column names have changed between versions of VGS. We will rename these columns so that they are consistent between years. 

```{r}
heber_2021_landscape_appearance <- heber_2021_landscape_appearance %>% 
  dplyr::rename(Site = SiteID) %>% 
  dplyr::rename(Sample = SampleNumber) %>% 
  dplyr::rename("Class Mid-Point" = nValue)
print(heber_2021_landscape_appearance)
```

The "Date" column was read in as a character vector. We want to convert the character vector into a datetime class.

```{r}
heber_2021_landscape_appearance$Date <- 
heber_2021_landscape_appearance %>% 
  pull(Date) %>% 
  lubridate::mdy()
print(heber_2021_landscape_appearance)
```

Create a new column "Year" to make this data consistent with data from other years.

```{r}
heber_2021_landscape_appearance <- 
  heber_2021_landscape_appearance %>% 
  dplyr::mutate(Year = year(heber_2021_landscape_appearance$Date))
print(heber_2021_landscape_appearance)
```

Write out this data now that it's been cleaned up and is consistent with data from previous years.

```{r}
readr::write_csv(heber_2021_landscape_appearance,
    file.path(path_to_user_folder,
              "grazing_data",
              "data",
              "landscape-appearance",
              "heber",
              "2021-heber-landscape-appearance-cleaned.csv"
  )
)
```
