---
title: "2022 Heber Report- Methods"
author: "Andrew Antaya"
date: "`r lubridate::now(tzone = 'US/Arizona')`"
output:
  bookdown::word_document2:
    toc: yes
    toc_depth: 3
    keep_md: yes
bibliography: references.bib
citation_package: biblatex
csl: rangeland-ecology-and-management.csl
link-citations: yes
editor_options:
  markdown:
    wrap: 72
---

# Methods

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      dpi = 300)
# knitr::opts_knit$set(root.dir = "~/grazing-interaction")

source("~/grazing-interaction/environment.R")
source("~/grazing-interaction/packages.R")
source("~/grazing-interaction/functions.R")

flextable::set_flextable_defaults(
  font.size = 10,
  theme_fun = theme_box,
  text.align = "center",
  fonts_ignore = TRUE,
  background.color = "#EFEFEF")
```

## Study Area

We conducted this study on the Black Mesa Ranger District of the
Apache-Sitgreaves National Forests, near Heber-Overgaard, in
east-central Arizona. This study took place on the \~19,500 acre Heber
Wild Horse Territory (HWHT) and off the territory on adjacent lands of
Black Mesa Ranger District of the A-S National Forests.

We monitored 2 grazing allotments, the Heber Allotment, consisting of
the Gentry, Bunger, and H.P. (Holding Pasture) pastures, and the Black
Canyon Allotment, consisting of the Sharp Hollow, King Phillip, and
Stermer pastures. Pastures may have some or all of their boundaries
within the HWHT. Practically speaking, it is difficult to delineate the
physical boundary of the HWHT, as no physical barrier prevents grazing
animals from entering or leaving the HWHT, rather grazing animals are
confined to boundaries of each pasture (breaks in fencing
notwithstanding). This report covers monitoring that occurred from June
2021 to November 2021. The University of Arizona has been monitoring
some of these sites since 2017 with data from these studies published in
previous reports.

```{r label='Map of Study Area', echo=FALSE, fig.cap='Location of Motion Cameras (Blue), Time-lapse Cameras (Red), and Addtional Vegetation Monitoring Sites (Green) within the Heber Wild Horse Territory (HWHT) and on adjacent lands of the Apache-Sitgreaves National Forests, Black Mesa Ranger District.'}

knitr::include_graphics(
  file.path("images/2021-Heber-Camera-and-Vegetation-Sites-University-of-Arizona.jpg"))

```

## Site Selection

### Motion Cameras

We selected motion camera monitoring sites using a stratified-random
design. We split the study area into two parts, pasture or portions of
pastures within the boundaries of the HWHT, and pastures or portions of
pastures that were outside of the HWHT. We generated random points for
each area that were stratified by Terrestrial Ecosystem Unit (TEUs) to
ensure that we captured a range of vegetation types on and off the HWHT.
From these stratified random points, we selected 15 sites on the HWHT
and 10 sites off the HWHT on adjacent lands. We chose an uneven
distribution of camera sites because our focus was on movements within
the HWHT and we wanted to prioritize capturing movements of animals
within the HWHT.

### Time-lapse Cameras

For time-lapse camera sites we selected 3 new sites in 2021 (Holding Pasture, Fire Lookout, and Only Ponderosa) as key areas based on the recommendations
of USFS Range Managers. Key areas are areas that a likely to show a
response to management actions
[@coulloudonUtilizationStudiesResidual1999]. Bear and Fifty-One were
time-lapse monitoring sites previously established in key areas in 2017
and 2019, respectively.

### Additional Vegetation Monitoring Sites

We then chose 5 more vegetation monitoring sites as key areas based on
feedback from USFS range management personnel. These key areas were
identified as areas of potential high use/congregation of horses based
on aerial observations of horses by USFS personnel conducted in 2021. We
recognize that these key areas may not be necessarily representative of
vegetation attributes for each pasture, but represent areas that are
potentially impacted by high use and are of concern for range managers. These high-use areas are also more likely to show a response to management actions when compared to low-use areas. 
To select these 5 additional sites, we first generated additional
stratified random points using the same criteria we used to select
motion camera sites. We then selected stratified random points that fell
within the key areas identified by USFS range management personnel.

```{r Heber Site Constructor, include=FALSE}
heber_2021_canopy_cover <-
  readr::read_csv(file.path(currentwd,
                          "data",
                          "canopy-cover",
                          "heber",
                          "2021-heber-canopy-cover-summarized-by-species.csv"))

heber_2021_canopy_cover <- heber_2021_canopy_cover %>%
  dplyr::rename(Site = SiteID)

heber_veg_sites <- heber_2021_canopy_cover %>%
  pull(Site) %>%
  unique() %>%
  as_tibble() %>%
  tidyr::drop_na() %>%
  dplyr::rename(Site = value)

# TODO move this outside of the notebook chunk

heber_veg_sites <- heber_veg_sites %>% dplyr::mutate(Allotment =
                                    dplyr::if_else(
                                      Site == "SHPT" |
                                        Site == "KPPJT" |
                                        Site == "STPO",
                                      "Black Canyon",
                                      "Heber")
                                  )

for (i in 1:nrow(heber_veg_sites)) {
  if (heber_veg_sites$Site[i] == "BRL") {
    heber_veg_sites$Pasture[i] <- "Bunger"
  } else if (heber_veg_sites$Site[i] == "A51") {
    heber_veg_sites$Pasture[i] <- "Bunger"
  } else if (heber_veg_sites$Site[i] == "OPO1") {
    heber_veg_sites$Pasture[i] <- "Bunger"
  } else if (heber_veg_sites$Site[i] == "HPT") {
    heber_veg_sites$Pasture[i] <- "HP"
  } else if (heber_veg_sites$Site[i] == "FLO1") {
    heber_veg_sites$Pasture[i] <- "Gentry"
  } else if (heber_veg_sites$Site[i] == "GETPBG") {
    heber_veg_sites$Pasture[i] <- "Gentry"
  } else if (heber_veg_sites$Site[i] == "GETO") {
    heber_veg_sites$Pasture[i] <- "Gentry"
  } else if (heber_veg_sites$Site[i] == "SHPT") {
    heber_veg_sites$Pasture[i] <- "Sharp Hollow"
  } else if (heber_veg_sites$Site[i] == "KPPJT") {
    heber_veg_sites$Pasture[i] <- "King Phillip"
  } else if (heber_veg_sites$Site[i] == "STPO") {
    heber_veg_sites$Pasture[i] <- "Stermer"
  }
}

for (i in 1:nrow(heber_veg_sites)) {
  if (heber_veg_sites$Site[i] == "BRL") {
    heber_veg_sites$`Within Territory`[i] <- "Yes"
  } else if (heber_veg_sites$Site[i] == "A51") {
    heber_veg_sites$`Within Territory`[i] <- "No"
  } else if (heber_veg_sites$Site[i] == "OPO1") {
    heber_veg_sites$`Within Territory`[i] <- "No"
  } else if (heber_veg_sites$Site[i] == "HPT") {
    heber_veg_sites$`Within Territory`[i] <- "No"
  } else if (heber_veg_sites$Site[i] == "FLO1") {
    heber_veg_sites$`Within Territory`[i] <- "Yes"
  } else if (heber_veg_sites$Site[i] == "GETPBG") {
    heber_veg_sites$`Within Territory`[i] <- "Yes"
  } else if (heber_veg_sites$Site[i] == "GETO") {
    heber_veg_sites$`Within Territory`[i] <- "No"
  } else if (heber_veg_sites$Site[i] == "SHPT") {
    heber_veg_sites$`Within Territory`[i] <- "Yes"
  } else if (heber_veg_sites$Site[i] == "KPPJT") {
    heber_veg_sites$`Within Territory`[i] <- "Yes"
  } else if (heber_veg_sites$Site[i] == "STPO") {
    heber_veg_sites$`Within Territory`[i] <- "No"
  }
}

for (i in 1:nrow(heber_veg_sites)) {
  if (heber_veg_sites$Site[i] == "BRL") {
    heber_veg_sites$`Time-Lapse Camera?`[i] <- "Yes"
  } else if (heber_veg_sites$Site[i] == "A51") {
    heber_veg_sites$`Time-Lapse Camera?`[i] <- "Yes"
  } else if (heber_veg_sites$Site[i] == "OPO1") {
    heber_veg_sites$`Time-Lapse Camera?`[i] <- "Yes"
  } else if (heber_veg_sites$Site[i] == "HPT") {
    heber_veg_sites$`Time-Lapse Camera?`[i] <- "Yes"
  } else if (heber_veg_sites$Site[i] == "FLO1") {
    heber_veg_sites$`Time-Lapse Camera?`[i] <- "Yes"
  } else if (heber_veg_sites$Site[i] == "GETPBG") {
    heber_veg_sites$`Time-Lapse Camera?`[i] <- "No"
  } else if (heber_veg_sites$Site[i] == "GETO") {
    heber_veg_sites$`Time-Lapse Camera?`[i] <- "No"
  } else if (heber_veg_sites$Site[i] == "SHPT") {
    heber_veg_sites$`Time-Lapse Camera?`[i] <- "No"
  } else if (heber_veg_sites$Site[i] == "KPPJT") {
    heber_veg_sites$`Time-Lapse Camera?`[i] <- "No"
  } else if (heber_veg_sites$Site[i] == "STPO") {
    heber_veg_sites$`Time-Lapse Camera?`[i] <- "No"
  }
}

print(heber_veg_sites)

heber_veg_sites_df <- as.data.frame(heber_veg_sites)
```

```{r label='Table-Heber-Veg-Sites-Summary', echo=FALSE, ft_show_coltype=FALSE, tab.cap="Vegetation monitoring sites were established in key areas identified by USFS range management personnel and were selected by a stratified random design based on Terrestrial Ecosystem Unit. At all 10 vegetation monitoring sites, we measured species canopy cover (i.e. Daubenmire) and landscape appearance. Sites with time-lapse cameras also received 5 grazing exclosures for estimating production and utilization with the paired-plot method."}

flextable::df_printer(heber_veg_sites_df)
```

### Paired-Plot

At the 5 time-lapse monitoring sites, we estimated production and
utilization with the paired-plot method
[@rexforddaubenmireCanopycoverageMethodVegetational1959] . We placed (5)
1 m^2^ grazing exclosures randomly at each site (except for the
Fifty-One site where we accidentally placed 6 exclosures). Establishing
grazing exclosures is labor intensive, and we were constrained to
monitoring 5 sites. We decided to establish grazing exlosure plots at
only the time-lapse sites with the intention of relating the paired-plot
estimates to the time-lapse camera data. Grazing exclosures plots were
established in June 2021 before summer monsoon rainfall and potential
corresponding vegetation response.

```{r label="Photo Grazing Exclosures at Bear", echo=FALSE, fig.cap="Example of three grazing exclosures at the Bear site, July 2021."}

knitr::include_graphics(
  file.path("images/2021-bear-exclosures.JPG"))

```

We clipped each of the (5) 1 m^2^ grazing exclosures in November 2021.
We used has two types of clipping methodologies. At the Only Ponderosa
site there was very little vegetation inside of the grazing exclosures
we clipped the entire 1 m^2^ exclosure plot. Therefore the bag weights
related to Only Ponderosa represent a larger clipped area than bags
clipped from other sites. We account for this difference in sample area
during analysis. At all other sites, we clipped (3) 40cm x 40cm
sub-plots inside of each 1 m^2^ exclosure plot. Clipping 3 sub-plots at
the center of each exclosure potentially negates any grazing that might
occur on the perimeter of the exclosure plot.

```{r Heber Paired Plot Site Summary, include=FALSE}
heber_paired_plot_2021_site_summary <-
readr::read_csv(file.path(currentwd,
                           "data",
                           "production",
                           "heber",
                           "csv",
                           "2021-heber-paired-plot-method1-site-summary.csv"))

n_exclosure_plots_clipped <-
heber_paired_plot_2021_site_summary %>%
  dplyr::filter(PlotType == "Exclosure") %>%
  mutate(SampleArea = dplyr::if_else(Site == "Only Ponderosa",
                                     "Entire 1 m² plot",
                                     "(3) 40 cm x 40 cm sub-plots",
                                     NA_character_)) %>%
  dplyr::select(-c("variable", "mean", "sd", "ci", "PlotType")) %>%
  dplyr::mutate(n = as.character(n)) %>%
  dplyr::rename("Number of Exclosure Plots" = n) %>%
  dplyr::rename("Clipped Sample Area" = SampleArea)
```


```{r Table-Heber-Paired-Plot-Site-Summary, echo=FALSE, ft_show_coltype=FALSE, tab.cap="Number of Exclosure Plots Clipped at Each Site."}

# ft <- flextable::flextable(n_exclosure_plots_clipped) %>%
#   flextable::autofit(add_w = 0.2, add_h = 0.2) %>%
#   flextable::align(align = "center", part = "all")
#
# flextable::body_add_flextable(ft)

flextable::df_printer(n_exclosure_plots_clipped)
```

Bags with grass clipping were dried at 60 °C for 48 hours. To get the
net weight of dried clippings in each bag, we subtracted the dried bag
weight when full of clippings from the bag weight when empty.

```{r Calculate Total Sample Area, include=FALSE}
# length of quadrat dimension X (in centimeters)
dim_x <- units::set_units(40, cm)

# length of quadrat dimension Y (in centimeters)
dim_y <- units::set_units(40, cm)

# calculate the area of the sampling frame in centimeters
sample_area_cm <- dim_x*dim_y

sample_area_m <- units::set_units(sample_area_cm, m^2)

# number of sampling frames/sub-plots
n_frames <- 3

# calculate total area of three 40cm x 40cm sub-plots
total_area_cm <- sample_area_cm*n_frames

# convert to meters squared
total_area_three_frames_m2 <-  set_units(total_area_cm, m^2)
```

We combined bag weights from 3 sub-plots together for each exclosure
plot (with the exception of the Only Ponderosa site). We converted the
bag weights to g/m^2^ by dividing the weight in grams by the area
sampled, `r total_area_three_frames_m2` m^2^ for all sites except for
the Only Ponderosa site, which was 1 m^2^. We estimated production at
each site by taking the average g/m^2^ for all exclosure plots at each
site.

```{r Calculate Sample Area 1 Frame, include=FALSE}
# length of quadrat dimension X (in centimeters)
dim_x <- units::set_units(40, cm)

# length of quadrat dimension Y (in centimeters)
dim_y <- units::set_units(40, cm)

# calculate the area of the sampling frame in centimeters
sample_area_cm <- dim_x*dim_y

sample_area_m <- units::set_units(sample_area_cm, m^2)

# number of sampling frames/sub-plots
n_frames <- 1

# calculate total area of three 40cm x 40cm sub-plots
total_area_cm <- sample_area_cm*n_frames

# convert to meters squared
total_area_one_frame_m2 <-  set_units(total_area_cm, m^2)
```

For the residual plots, we randomly placed (10) 40cm x 40cm plots at
each site in November 2021 at the same time when we clipped the
exclosure plots. We clipped, dried, and weighed each residual plot using
the same methods as we did for the exclosure plots. We converted bag
weights to g/m^2^ by dividing the weight in grams by the area sampled
`r total_area_one_frame_m2` m^2^. We estimated the amount of vegetation
remaining at each site by taking the average g/m^2^ for all residual
plots at each site. We then converted from g/m^2^ to lbs/acre^2^. To
estimate utilization, we divided the average production at each site by
the average residual amount remaining at each site.

## Daubenmire

At all 10 vegetation monitoring sites, we also estimated plant cover by
species with the Daubenmire method
[@rexforddaubenmireCanopycoverageMethodVegetational1959]. At each
vegetation monitoring site, we established (2) 50-pace linear transects,
parallel and separated by 5-paces, starting at the GPS point. We used a
40 cm x 40 cm handled sampling frame typical for rangeland monitoring.
We did not use the 20 cm x 50 cm frame described by
@rexforddaubenmireCanopycoverageMethodVegetational1959 because in
practice, handled sampling frames are more efficiently used than 20cm x
50 cm frames. We placed the sampling frame centered at the point nearest
to our right foot, and each point was separated by 1 pace. We then
estimated the percentage of each frame occupied by each plant species as
1 of 6 classes, 0-5%, 5-25%, 25-50%, 50-75%, 75-95%, and 95-100%
[@rexforddaubenmireCanopycoverageMethodVegetational1959] . Where we
could not reliably establish species, we used plant genius instead. We
summarized plant cover at each site by averaging the class mid-point for
each species detected at each site.

```{r Photo Monitoring GETPBG, echo=FALSE, fig.cap="Monitoring At the GETPBG site, November 2021."}

knitr::include_graphics(
  file.path("images/monitoring-GETPBG.jpg"))

```

## Landscape Appearance

At all 10 vegetation monitoring sites, we also estimated utilization
from the landscape appearance method. It is important to note that
landscape appearance appears to give a *quantitative* estimate of
utilization but in reality is a *qualitative* estimate of utilization
[@smithGuideRangelandMonitoring2012]. We recorded 1 landscape appearance
observation every 10 paces along each 50-pace transect while recording
plant cover by species (i.e. Daubenmire method) for a total of 10
landscape appearance observations per site. At each landscape appearance
observation, we estimated the percent utilization based on written
descriptions of 7 classes [@coulloudonUtilizationStudiesResidual1999].
We calculated the average percent utilization at each site by taking the
average of the class mid-point.

## Literature Cited [Placeholder]
