---
title: "2021 Heber Paired-Plot Analysis"
author: "Andrew Antaya"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document:
    toc: yes
  citation_package: biblatex
  html_document:
    theme: readable
    toc: yes
    toc_depth: 5
    fig_caption: yes
  pdf_document: default
subtitle:
bibliography: My Library.bib
link-citations: yes
editor_options:
  markdown:
    wrap: 72
---
# Setup

```{r setup}
source("~/grazing-interaction/environment.R")
source("~/grazing-interaction/packages.R")
source("~/grazing-interaction/functions.R")
```

```{r knitr setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = currentwd)
```

## Load Data

```{r Load Heber Production Data}
heber_production_2021 <- readr::read_csv(
  file.path(currentwd,
            "data",
            "production",
            "heber",
            "csv",
            "2021-heber-production-cleaned.csv"),
  col_names = TRUE,
  na = c(""," ","NA"))
print(heber_production_2021)
```

## Data Clean Up

The code expects a column called "TotalDryWt" that we need to add to the Heber data. This column usually is for row sums for each bag from a sub-plot, but in this case there aren't any sub-plots so we will set the "Bag1NetWt" column to equal the new "TotalDryWt" column.

```{r Add "TotalDryWt" to Heber Data}
heber_production_2021 <- heber_production_2021 %>% 
  dplyr::mutate(TotalDryWt = Bag1NetWt)
print(heber_production_2021)
```

```{r temp}
heber_paired_plot_2021 <- heber_production_2021
```

## Unit Conversion

The production data has two types of clipping methodologies which could lead to confusion. At the "Only Ponderosa" site we clipped the entire 1m^2^ exclosure plot, which means that the bag weights related to the Only Ponderosa site represent a larger clipped area than bags clipped from other sites. 

| Site            | How much was clipped?    | Number of Exclosure Plots |
|-----------------|--------------------------|---------------------------|
| Only Ponderosa  | Entire 1m^2^             | 5                         |
| Holding Pasture | (3) 40cm x 40cm quadrats | 5                         |
| Fire Lookout    | (3) 40cm x 40cm quadrats | 5                         |
| Bear            | (3) 40cm x 40cm quadrats | 5                         |
| Area Fifty One  | (3) 40cm x 40cm quadrats | 6                         |


At all other sites, we clipped (3) 40cm x 40cm plots inside of each 1m^2^ exclosure plot, which means we can take an average sub-sample weight for each plot, and then either use the sub-sample average to generate average weight per 40cm quadrat (Method 2), or we can add together the three sub-sample weights and divide by their combined area to get a weight per m^2^ (Method 1).

### Set and Convert Units to m^2^

```{r Set Quadrat Size}
# length of quadrat dimension X (in centimeters)
dim_x <- units::set_units(40, cm)

# length of quadrat dimension Y (in centimeters)
dim_y <- units::set_units(40, cm)

# calculate the area of the sampling frame in centimeters
sample_area_cm <- dim_x*dim_y

print(sample_area_cm)
```

Now we convert to grams per meter[^2] which is traditionally how paired-plot data is represented in rangelands research.

```{r convert g/cm^2 to g/m^2}
sample_area_m <- units::set_units(sample_area_cm, m^2)
print(sample_area_m)
```

Next, find the total area of (3) 40cm x 40cm quadrats in centimeters[^2]. We sub-sampled each exclosure by clipping 3 plots (with the execption of the Only Ponderosa site where we clipped the entire exclosure).

```{r Find Total Area from N Quadrats}
# number of sampling frames/quadrats
n_frames <- 3

# calculate total area of three 40cm x 40cm quadrats
total_area_cm <- sample_area_cm*n_frames

print(total_area_cm)
```

Convert from centimeters[^2] to meters[^2]. This is total area sampled by three 40cm x 40cm quadrats.

```{r Convert Area from cm to m}
total_area_m2 <-  set_units(total_area_cm, m^2)

print(total_area_m2)
```

Take the reciprocal of the total area sampled by 3 quadrats. We want to know how much we need to multiply by get the total area sampled by three 40cm x 40cm quadrats to equal 1 m^2^.

```{r Three Frame Conversion Value}
three_frame_conversion <- as.numeric(1/total_area_m2)

print(three_frame_conversion)
```

## Summary Statistics

### Method 1- Sub-Plots Combined

This method combines the (3) sub-plots from within each exclosure by addition, and it *does not* generate an average weight for the sub-plots as Method 2 does. Method 1 will likely generate less error because we are not taking an average of an average, as we do in Method 2.

Here we group the data frame by site and plot, which generates 26 groups, a group for each site, and a group for each plot. Then we summarize the weight for each plot by adding together each sub-plot. We also use the `units` package to set the weight to grams. Setting units now will help us convert to grams per meter[^2] in a future step. And it's also nice to show what measurement units we are dealing with.

```{r summarize exclosure plots by subsample}
heber_production_2021_method1 <- 
heber_production_2021 %>% 
  dplyr::filter(PlotType == "Exclosure") %>% 
  dplyr::group_by(Site, Plot) %>% 
  dplyr::summarize(TotalDryWt = sum(units::set_units(TotalDryWt, g)))
print(heber_production_2021_method1)
```

As we mentioned, we sampled the entire 1 m[^2] plot at the Only Ponderosa site. We will create a new column called `SampleArea` which represents the area sampled for each exclosure plot at each site. Here we set the units for the `SampleArea` column for the "Only Ponderosa" site, using 1 m[^2], because if we didn't, it would greatly overestimate the amount of production at the Only Ponderosa site. All other sites were set to 0.48 m[^2], as we sub-sampled each plot with (3) 40 cm x 40 cm sub-plots.

```{r adjust area sampled for only ponderosa site}
heber_production_2021_method1 <- 
heber_production_2021_method1 %>% 
  dplyr::mutate(SampleArea = dplyr::if_else(Site == "Only Ponderosa", # condition
                                            units::set_units(1, m^2), # if true
                                            units::set_units(total_area_m2, m^2), # if false
                                            NA_real_) # if missing
  )
print(heber_production_2021_method1)
```

Now that we have a column representing `SampleArea` and we can calculate the grams per meter[^2] for each exclosure.

```{r add "GramsPerMeter" column for summarized by sub-sample}
heber_production_2021_method1 <- 
heber_production_2021_method1 %>% 
  mutate(GramsPerMeter = TotalDryWt / SampleArea)
print(heber_production_2021_method1)
```

Calculate summary statistics for exclosure plots by site using the `rstatix` package.

```{r calc summary stats for summarized by subsample}
heber_production_2021_method1 <- 
heber_production_2021_method1 %>% 
  group_by(Site) %>% 
  rstatix::get_summary_stats(GramsPerMeter, 
                             type = "common", 
                             show = c("n","mean","sd","ci"))
print(heber_production_2021_method1)
```

```{r set units on descriptive statistics method 1}
heber_production_2021_method1 <- 
heber_production_2021_method1 %>% 
  dplyr::mutate(sd = set_units(sd, g/m^2)) %>% 
  dplyr::mutate(ci = set_units(ci, g/m^2))
print(heber_production_2021_method1)
```

```{r convert GramsPerMeter to LbsPerAcre method 1}
heber_production_2021_method1 <- 
heber_production_2021_method1 %>% 
  dplyr::mutate(mean = set_units(mean, lb/acre)) %>% 
  dplyr::mutate(sd = set_units(sd, lb/acre)) %>% 
  dplyr::mutate(ci = set_units(ci, lb/acre))
print(heber_production_2021_method1)
```

### Method 2- Sub-Plots Separate

Method 2 calculates are average for each exclosure plot by averaging the weights sampled by 3 sub-plots from within each exclosure plot. This will likely create more error because we are using an sub-plot average to then generate an estimate for each plot, then we average plots together to generate a production estimate for each site (an average of an average).

I am performing this method as an experiment to understand how the error compounds.

First we will create an object that is a copy of the production data so we can experiment without altering the original data.

```{r create copy of production data method 2}
heber_production_2021_method2 <- heber_production_2021
```

Then we set the units for the weights of each sub-plot using the `units` package. Each bag represents the net weight (Total Weight of Bag + Clippings - Weight of Bag = Net Weight Clippings) that were dried in an oven at 60 deg C for at least 48 hours.

```{r set units for each sub-plot method 2}
heber_production_2021_method2$TotalDryWt <- heber_production_2021_method2 %>% 
  pull(TotalDryWt) %>% 
  units::set_units("g")
print(heber_production_2021_method2)
```

The `MethodType` column represents whether we clipped the entire exclosure plot ("Entire Plot"), or if we clipped 3 sub-plots inside of each exclosure ("Sub Plots"). Create a new column `SampleArea` that represents the area sampled by _each sub-plot_. Since we mixed-methods and clipped the entire plot at Only Ponderosa, we will set that to equal 1 m[^2] and all the other sub-plots to equal (1) 40cm x 40cm quadrat.

```{r create "SampleArea" column for each sub-plot method 2}
heber_production_2021_method2 <- heber_production_2021_method2 %>% 
  dplyr::filter(PlotType == "Exclosure") %>% 
  dplyr::mutate(SampleArea = if_else((PlotType == "Exclosure" & MethodType == "Sub Plots"),
                                     sample_area_m, # true
                                     1, # false
                                     NA_real_) # missing
                )
print(heber_production_2021_method2)
```

Then we create a column with the grams per meter[^2].

```{r add "GramsPerMeter" column for each sub-plot method 2}
heber_production_2021_method2 <- 
  heber_production_2021_method2 %>% mutate(GramsPerMeter = TotalDryWt / SampleArea)
print(heber_production_2021_method2)
```

And then convert grams per meter[^2] to pounds per acre so we can use units more commonly used in rangeland management when discussion production at the pasture scale.

```{r convert "GramsPerMeter" to "LbsPerAcre" method 2}
heber_production_2021_method2 <- heber_production_2021_method2 %>% 
  mutate(LbsPerAcre = set_units(GramsPerMeter, lb/acre))
print(heber_production_2021_method2)
```

Calculate the summary stats for Method 2 using the sub-plot averages to generate an average production estimate for each plot. Similar to Method 1, we are grouping by site and plot and then getting summary stats using the `rstatix` package.

```{r calc summary stats for each plot using sub-plot averages}
heber_production_2021_method2_subplot_summary <- heber_production_2021_method2 %>% 
  dplyr::filter(PlotType == "Exclosure") %>% 
  group_by(Site, Plot) %>% 
  rstatix::get_summary_stats(GramsPerMeter, 
                             type = "common", 
                             show = c("n", "mean", "sd", "ci"))
print(heber_production_2021_method2_subplot_summary)
```

Then we generate an average production estimate for each site by averaging the plots.

```{r calc summary stats for each site using plot averages}
heber_production_2021_method2_site_summary <- heber_production_2021_method2_subplot_summary %>% 
  group_by(Site) %>% 
  rstatix::get_summary_stats(mean,
                             type = "common", 
                             show = c("n", "mean", "sd", "ci"))
print(heber_production_2021_method2_site_summary)
```

Set the units for the standard deviation and the confidence interval using the `units` package. Setting the units for these descriptive statistics helps us understand the variability and spread of the data in relateable units.

```{r set units on descriptive statistics method 2}
heber_production_2021_method2_site_summary <- heber_production_2021_method2_site_summary %>%
  dplyr::mutate(sd = set_units(sd, g/m^2)) %>% 
  dplyr::mutate(ci = set_units(ci, g/m^2))
print(heber_production_2021_method2_site_summary)
```

## Compare Methods

Now that we've generated production estimates for each site using two different methods, we want to compare the results of the two methods together and see which method generates more reliable estimates (i.e. less error/more precision).




### Plot Production

```{r}
heber_production_2021_method1$mean <- 
  heber_production_2021_method1$mean %>% as.numeric()

heber_production_2021_method1$sd <- 
  heber_production_2021_method1$sd %>% as.numeric()

heber_production_2021_method1$ci <- 
  heber_production_2021_method1$ci %>% as.numeric()

print(heber_production_2021_method1)
```

```{r}
heber_production_stats_as_numeric_2021 <- heber_production_2021_method1
```

```{r}
heber_production_stats_as_numeric_2021 %>% 
ggplot(aes(x = Site, y = mean, fill = Site)) +
  geom_col() +
  geom_errorbar(aes(ymin = (mean - ci), 
                    ymax = (mean + ci)), 
                position = position_dodge(0.5), 
                width = 0.25) +
  labs(title = expression(atop("Heber Wild Horse Territory", 
                               paste("Production (Pounds per Acre)"))), 
       subtitle = "2021") +
  ylab("Production (lbs/acre) ± 95% CI") +
  scale_y_continuous(limits = c(-200, 3000), breaks = seq(0, 3000, by = 500)) +
  theme(plot.title = element_text(hjust = 0.5, size = 11),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 0, r = 0, b = 5, l = 0)),
        axis.text.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 10)),
        axis.ticks = element_blank(),
        legend.position = "none") +
  annotate(geom = "text", 
           x = 1, 
           y = (heber_production_stats_as_numeric_2021$mean[1] + 
                  heber_production_stats_as_numeric_2021$ci[1] + 200), 
           label = signif(heber_production_stats_as_numeric_2021$mean[1], 2)) +
  annotate(geom = "text", 
           x = 2, 
           y = (heber_production_stats_as_numeric_2021$mean[2] + 
                  heber_production_stats_as_numeric_2021$ci[2] + 200), 
           label = signif(heber_production_stats_as_numeric_2021$mean[2], 2)) +
  annotate(geom = "text", 
           x = 3, 
           y = (heber_production_stats_as_numeric_2021$mean[3] + 
                  heber_production_stats_as_numeric_2021$ci[3] + 200), 
           label = signif(heber_production_stats_as_numeric_2021$mean[3], 2)) +
  annotate(geom = "text", 
           x = 4, 
           y = (heber_production_stats_as_numeric_2021$mean[4] + 
                  heber_production_stats_as_numeric_2021$ci[4] + 200), 
           label = signif(heber_production_stats_as_numeric_2021$mean[4], 2)) +
  annotate(geom = "text", 
           x = 5, 
           y = (heber_production_stats_as_numeric_2021$mean[5] + 
                  heber_production_stats_as_numeric_2021$ci[5] + 200), 
           label = signif(heber_production_stats_as_numeric_2021$mean[5], 2))
ggsave(filename = "2021-heber-production.jpg",
       path = file.path("figures", "production", "heber"),
       width = 9,
       height = 6,
       units = "in")
```

```{r}
# heber_production_2021 <- heber_production_2021 %>% 
#   dplyr::mutate(SampleArea = if_else((PlotType == "Residual"),
#                                      sample_area_m, # true
#                                      1, # false
#                                      NA_real_) # missing
#                 )
# print(heber_production_2021)
```


