---
title: "2021 Heber Daubenmire Analysis"
author: "Andrew Antaya"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
    theme: readable
    toc: yes
    toc_depth: 5
    fig_caption: yes
  citation_package: biblatex
  word_document:
    toc: yes
  pdf_document: default
subtitle: Analysis
zotero: "My Library"
link-citations: yes
editor_options: 
  markdown: 
    wrap: 72
---

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      dpi = 300)
knitr::opts_knit$set(root.dir = "~/grazing-interaction")

source("~/grazing-interaction/environment.R")
source("~/grazing-interaction/packages.R")
source("~/grazing-interaction/functions.R")

flextable::set_flextable_defaults(
  font.size = 10, 
  theme_fun = theme_box,
  text.align = "center",
  fonts_ignore = TRUE,
  background.color = "#EFEFEF")
```

## Load Data

```{r read csv}
canopy_cover_df <- readr::read_csv(
  file.path(path_to_temp_data, 
            "canopy-cover", 
            "heber", 
            "2021-heber-canopy-cover.csv")
  )
```

```{r}
print(canopy_cover_df)
```

## Convert the `Date` column to a Datetime class.

```{r convert Date column to date class}
canopy_cover_df <- canopy_cover_df %>% dplyr::mutate(Date = lubridate::mdy(Date))

# check that the date parsed correctly and is a Datetime
str(canopy_cover_df$Date)
```

## Arrange Data from Oldest to Newest Observation Date

```{r arrange by date from oldest to newest}
canopy_cover_df <- canopy_cover_df %>% dplyr::arrange(Date)

print(canopy_cover_df)
```

We will create a pre-monsoon and post-monsoon categorical variables that
we can use to conveniently handle the surveys that took place in June
2021 (pre-monsoon) and the surveys that took place in November 2021
(post-monsoon). These categorical variables will be used as groups for
plotting purposes.

The timing of the vegetation surveys is important. The surveys that took
place in June 2021 represent within-season use, and the surveys that
took place in November 2021 represent end-of-season use. We would expect
that vegetation attributes measured during June 2021 would have a
significant response to rainfall in July/August, and then would be
grazed for the remainder of the grazing season.

Any observations take before July 1st 2021 will be the placed in the
"June" category, and any dates after July 1st 2021 will be placed in the
"November" category.

```{r add Month column}
canopy_cover_df <- 
canopy_cover_df %>% dplyr::mutate(Month = dplyr::if_else(Date < "2021-07-01", 
                                  "June", 
                                  "November"),
                                  .after = Date
                                  )
```

How many observations were from June, and how many observations were
from November?


Convert the `Month` column into a categorical factor. Factors will be treated as groups by ggplot2 when it comes to plotting.

```{r convert Month column to factor}
canopy_cover_df$Month <- 
canopy_cover_df %>% 
  pull(Month) %>% 
  forcats::as_factor() 
```

Check that the `Month` column is indeed a factor with 2 levels.

```{r check Month column factor levels}
str(canopy_cover_df$Month)
```

## Split the Data into Two Groups

The percent canopy cover for every plant species is recorded inside of each Daubenmire frame when using the Daubenmire frame. 

For comparing sample sizes, we will split the data into two groups: observations that occured in June 2021 and observations that occurred in November 2021.

```{r split observations by Month}
june_observations <- canopy_cover_df %>% dplyr::filter(Month == "June")

november_observations <- canopy_cover_df %>% dplyr::filter(Month == "November")
```

There were `r june_observations %>% nrow()` from June 2021 and
`r november_observations %>% nrow()` from November 2021. It's
interesting to see the number of observations from each group, as there were more
observations in November than in June. There are more observations in November because the plants respond to summer monsoon rainfall, grow and spread.

When it comes to statistical testing, this is called an "unbalanced research design". This is not something we could anticipate before sampling, so we will investigate this further.

## Summary Stats for Canopy Cover

```{r summary stats}
summary_stats <- 
canopy_cover_df %>% 
  group_by(Month, SiteID, SpeciesSymbol) %>% 
  rstatix::get_summary_stats(nValue, type = "common")
print(summary_stats)
```

### Potential Reasons for Differences in Species at the Same Site between Sampling Sessions

Each site has different species present/detected, but species may change
from June to November. I think this is most likely with annual forbs and
annual grasses, which we group into their own categories, but it is also
possible with perennial species for a number of potential reasons:

1.  Species Not Detected (Missed) During First Sampling but Present at
    Site (Sampling Error)
    1.1  More likely for uncommon or rare species
    1.2  Mitigated by increasing the number of samples or multiple samples per sampling period
    1.3  It's also possible that we started and ended each transect from different places
    1.4  It's also possible that we paced each transect differently and missed some species
2.  Species Newly Established at Site Between First and Second Sampling Sessions
    2.1  Annual grasses and annual forbs establish after rainfall
    2.2  Perennials can establish too
    2.3  This problem would be called "closure" in hierarchical models
3.  Mis-identification of the Species
    3.1 Mis-identification can happen at either sampling session

Let's do a little exploratory data analysis to understand how the species detected at each site changes from June to November.

Let's see how species change at the Fifty One site from June to November.

# TODO I want to compare which species were at each site during June and November, which species were detected only in June, and which species were detected only in November

```{r}
canopy_cover_df %>% 
  dplyr::filter(SiteID == "A51") %>% 
  dplyr::group_by(Month, SpeciesSymbol) %>% 
  dplyr::count()
```

```{r}
fiftyone_june_count <- 
  canopy_cover_df %>% 
  dplyr::filter(SiteID == "A51" & Month == "June") %>%
  dplyr::count(SpeciesSymbol)
print(fiftyone_june_count)
```

```{r}
fiftyone_november_count <- 
  canopy_cover_df %>% 
  dplyr::filter(SiteID == "A51" & Month == "November") %>% 
  dplyr::count(SpeciesSymbol)
print(fiftyone_november_count)
```

```{r}
fiftyone_june_count$SpeciesSymbol %in% fiftyone_november_count$SpeciesSymbol
```

```{r}
fiftyone_species_detected_in_june_but_not_in_november <- fiftyone_june_count %>% 
  dplyr::filter(fiftyone_june_count$SpeciesSymbol %in% fiftyone_november_count$SpeciesSymbol == FALSE)
print(fiftyone_species_detected_in_june_but_not_in_november)
```

```{r}
fiftyone_november_count$SpeciesSymbol %in% fiftyone_june_count$SpeciesSymbol
```

```{r}
fiftyone_species_detected_in_november_but_not_in_june <- fiftyone_november_count %>% 
  dplyr::filter( fiftyone_november_count$SpeciesSymbol %in% fiftyone_june_count$SpeciesSymbol == FALSE)
print(fiftyone_species_detected_in_november_but_not_in_june)
```

```{r}
canopy_cover_grouped_by_site_and_month <- 
canopy_cover_df %>% 
  dplyr::group_by(SiteID, Month) %>% 
  dplyr::count(SpeciesSymbol)
print(canopy_cover_grouped_by_site_and_month)
```

```{r}
list_of_tibbles_by_site_and_month <- 
  canopy_cover_grouped_by_site_and_month %>% 
  dplyr::group_split()
print(list_of_tibbles_by_site_and_month)
```

Compare which species occur in June.

```{r current chunk}
site <- list_of_tibbles_by_site_and_month[[1]] %>% 
  pull(SiteID) %>% 
  unique()

month <- list_of_tibbles_by_site_and_month[[1]] %>% 
  pull(Month) %>%
  as.character() %>% 
  unique()

glue::glue(site, "_", month)
```


```{r}

```


#### Research Question

If the species is present at BOTH the June sampling session AND the November sampling session, is there a change in % canopy cover for that species?

H0: There is no change in mean canopy cover for a given species (at a given site).
H1: There is a difference in mean canopy cover for a given species (at a given site).

Why might we care about if there is a change? 

1.  Management actions, (e.g. grazing might) might be affecting changes in canopy cover
2.  Environmental conditions (e.g. rainfall) (which are out of the control of resource managers) may be driving changes
3.  Probably a combination of both!

What do we really care about?
1.  Special plant species that might be rare, endangered, or indicators of high site quality (or conversely low site quality- invasive species)
2.  How management actions drive changes in canopy cover
3.  

Need to pair the species from June with the same species from November.

#### Species That Are Detected in June AND November for Each Site

```{r}
canopy_cover_df %>% dplyr::group_by(SiteID, SpeciesSymbol) %>% dplyr::filter(Month == "June") %>% dplyr::filter(Month == "November")
```



Select 1 site, 1 species, and do a t-test.

```{r}
fifty_one_annual_forbs <- 
canopy_cover_df %>% dplyr::ungroup() %>% dplyr::filter(SiteID == "A51" & SpeciesSymbol == "AAFF")

print(fifty_one_annual_forbs)
```

```{r}
fifty_one_annual_forbs %>% 
  rstatix::pairwise_t_test(nValue ~ Month) %>% 
  rstatix::add_significance()
```

# TODO plot a boxplot or violin plot for the A51 annual forb example

```{r}
stat_test <- canopy_cover_df %>% 
  rstatix::t_test(nValue ~ Month, paired = TRUE)
print(stat_test)
```

