---
title: "2021 Heber Daubenmire Analysis"
author: "Andrew Antaya"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
    theme: readable
    toc: yes
    toc_depth: 5
    fig_caption: yes
  citation_package: biblatex
  word_document:
    toc: yes
  pdf_document: default
subtitle: Analysis
zotero: "My Library"
link-citations: yes
editor_options: 
  markdown: 
    wrap: 72
---

# Setup

```{r}
currentwd <- "/home/rstudio/grazing-interaction"
```

```{r setup}
source(file.path(currentwd, "environment.R"))
source(file.path(currentwd, "packages.R"))
source(file.path(currentwd, "functions.R"))
```

```{r knitr setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = currentwd)
```

# Load Data

```{r}
canopy_cover_df <- readr::read_csv(file.path(path_to_data_input_folder, "canopy-cover", "2021-heber-canopy-cover.csv"))
```

```{r}
print(canopy_cover_df)
```

## Convert the `Date` column to a Datetime class.

```{r}
canopy_cover_df <- canopy_cover_df %>% dplyr::mutate(Date = lubridate::mdy(Date))

# check that the date parsed correctly and is a Datetime
str(canopy_cover_df$Date)
```

## Arrange Data from Oldest to Newest Observation Date

```{r}
canopy_cover_df <- canopy_cover_df %>% dplyr::arrange(Date)

print(canopy_cover_df)
```

We will create a pre-monsoon and post-monsoon categorical variables that
we can use to conveniently handle the surveys that took place in June
2021 (pre-monsoon) and the surveys that took place in November 2021
(post-monsoon). These categorical variables will be used as groups for
plotting purposes.

The timing of the vegetation surveys is important. The surveys that took
place in June 2021 represent within-season use, and the surveys that
took place in November 2021 represent end-of-season use. We would expect
that vegetation attributes measured during June 2021 would have a
significant response to rainfall in July/August, and then would be
grazed for the remainder of the grazing season.

Any observations take before July 1st 2021 will be the placed in the
"June" category, and any dates after July 1st 2021 will be placed in the
"November" category.

```{r}
canopy_cover_df <- 
canopy_cover_df %>% dplyr::mutate(Month = dplyr::if_else(Date < "2021-07-01", 
                                  "June", 
                                  "November"),
                                  .after = Date
                                  )
```

How many observations were from June, and how many observations were
from November?

```{r}
june_observations <- canopy_cover_df %>% dplyr::filter(Month == "June")

november_observations <- canopy_cover_df %>% dplyr::filter(Month == "November")
```

There were `r june_observations %>% nrow()` from June 2021 and
`r november_observations %>% nrow()` from November 2021. It's
interesting to see the distribution of observations, as there were more
observations in November than in June. We will investigate this further.

## Summary Stats for Canopy Cover

```{r}
summary_stats <- 
canopy_cover_df %>% 
  group_by(Month, SiteID, SpeciesSymbol) %>% 
  rstatix::get_summary_stats(nValue, type = "common")
print(summary_stats)
```

```{r}
summary_stats %>% dplyr::filter(SiteID == "A51" & SpeciesSymbol == "AAFF")
```
### Potential Reasons for Differences in Species at the Same Site between Sampling Sessions

Each site has different species present/detected, but species may change
from June to November. I think this is most likely with annual forbs and
annual grasses, which we group into their own categories, but it is also
possible with perennial species for a number of potential reasons:

1.  Species Not Detected (Missed) During First Sampling but Present at
    Site
    1.1  More likely for uncommon or rare species
    1.2  Mitigated by increasing the number of samples or multiple samples per sampling period
2.  Species Newly Established at Site Between First and Second Sampling Sessions
    2.1  Annual grasses and annual forbs establish after rainfall
    2.2  Perennials can establish too
    2.3  This problem would be called closure in hierachical models
3.  Mis-identification of the Species
4.  Random-ness from sampling
    4.1  It's also possible that we started and ended each transect from different places
    4.2  It's also possible that we paced each transect differently and missed some species

Let's do a little exploratory data analysis to understand how the species detected at each site changes from June to November.

Let's see how species change at the Fifty One site from June to November.

```{r}
canopy_cover_df %>% 
  dplyr::filter(SiteID == "A51") %>% 
  dplyr::group_by(Month, SpeciesSymbol) %>% 
  dplyr::count()
```

```{r}
fiftyone_june_count <- 
  canopy_cover_df %>% 
  dplyr::filter(SiteID == "A51" & Month == "June") %>%
  dplyr::count(SpeciesSymbol)
print(fiftyone_june_count)
```

```{r}
fiftyone_november_count <- 
  canopy_cover_df %>% 
  dplyr::filter(SiteID == "A51" & Month == "November") %>% 
  dplyr::count(SpeciesSymbol)
print(fiftyone_november_count)
```

```{r}
fiftyone_june_count$SpeciesSymbol %in% fiftyone_november_count$SpeciesSymbol
```

```{r}
fiftyone_species_detected_in_june_but_not_in_november <- fiftyone_june_count %>% 
  dplyr::filter(fiftyone_june_count$SpeciesSymbol %in% fiftyone_november_count$SpeciesSymbol == FALSE)
print(fiftyone_species_detected_in_june_but_not_in_november)
```

```{r}
fiftyone_november_count$SpeciesSymbol %in% fiftyone_june_count$SpeciesSymbol
```

```{r}
fiftyone_species_detected_in_november_but_not_in_june <- fiftyone_november_count %>% 
  dplyr::filter( fiftyone_november_count$SpeciesSymbol %in% fiftyone_june_count$SpeciesSymbol == FALSE)
print(fiftyone_species_detected_in_november_but_not_in_june)
```

#### Research Question

If the species is present at BOTH the June sampling session AND the November sampling session, is there a change in % canopy cover for that species?

H0: There is no change in mean canopy cover for a given species (at a given site).
H1: There is a difference in mean canopy cover for a given species (at a given site).

Why might we care about if there is a change? 

1.  Management actions, (e.g. grazing might) might be affecting changes in canopy cover
2.  Environmental conditions (e.g. rainfall) (which are out of the control of resource managers) may be driving changes
3.  Probably a combination of both!

What do we really care about?
1.  Special plant species that might be rare, endangered, or indicators of high site quality (or conversely low site quality- invasive species)
2.  How management actions drive changes in canopy cover
3.  

Need to pair the species from June with the same species from November.

#### Species That Are Detected in June AND November for Each Site

```{r}
canopy_cover_df %>% dplyr::group_by(SiteID, SpeciesSymbol) %>% dplyr::filter(Month == "June") %>% dplyr::filter(Month == "November")
```

```{r}
stat_test <- canopy_cover_df  %>% 
  dplyr::group_by(SiteID, SpeciesSymbol, Month)
  t_test(nValue ~ Month, paired = TRUE) %>%
  add_significance()
stat.test
```

```{r}
stat_test <- canopy_cover_df  %>% 
  group_by(Month, SiteID, SpeciesSymbol)
print(stat_test)
```

