---
title: "2021-heber-landscape-appearance-preprocessing"
author: "Andrew Antaya"
date: "4/16/2022"
output:
  html_document: 
    theme: readable
    toc: yes
    toc_depth: 5
    fig_caption: yes
  word_document:
    toc: yes
---

# Setup

First, let's remove all objects from the environment to start fresh each time.

```{r clear environment, eval=FALSE}
rm(list = ls(all = TRUE))
```

```{r setup environment}
source(file.path("", "home", "rstudio", "grazing-interaction", "environment.R"))
```

```{r knitr setup, include=FALSE}
knitr::opts_knit$set(root.dir = currentwd)
```

# Load Data

```{r Load 2021 Heber Landscape Appearance Data}
heber_2021_landscape_appearance <- readr::read_csv(
    file.path(
        getwd(), "data", "vegetation",
        "heber", "landscape-appearance",
        "2021-heber-landscape-appearance-vgs.csv"
    ),
    col_names = TRUE, na = c("", " ", "NA")
)

print(heber_2021_landscape_appearance)
```

# Clean Data

## Remove Unnecessary Columns

```{r}
heber_2021_landscape_appearance <- heber_2021_landscape_appearance %>% 
  dplyr::select(-c("X1", "ProtocolType", "FormName", "Element"))
print(heber_2021_landscape_appearance)
```

## Rename Columns 

Some of the column names have changed between versions of VGS. We will rename these columns so that they are consistent between years. 

```{r}
heber_2021_landscape_appearance <- heber_2021_landscape_appearance %>% 
  dplyr::rename(Site = SiteID) %>% 
  dplyr::rename(Sample = SampleNumber) %>% 
  dplyr::rename("Class Mid-Point" = nValue)
print(heber_2021_landscape_appearance)
```

The "Date" column was read in as a character vector. We want to convert the character vector into a datetime class. 

```{r}
heber_2021_landscape_appearance$Date <- 
heber_2021_landscape_appearance %>% 
  pull(Date) %>% 
  lubridate::mdy()
print(heber_2021_landscape_appearance)
```

Create a new column "Year" to make this data conistent with data from other years.

```{r}
heber_2021_landscape_appearance <- 
  heber_2021_landscape_appearance %>% 
  dplyr::mutate(Year = year(heber_2021_landscape_appearance$Date))
print(heber_2021_landscape_appearance)
```

Write out this data now that it's been cleaned up and is consistent with data from previous years.

```{r}
readr::write_csv(heber_2021_landscape_appearance,
  file.path(
    getwd(), "data", "vegetation",
    "heber", "landscape-appearance",
    "csv", "2021-heber-landscape-appearance.csv"
  )
)
```

