---
title: "R Notebook"
output: html_notebook
---

Clear the R environment to start from a clean slate.

```{r}
# clear the environment
rm(list=ls(all=TRUE))
```

Read in the required packages from another R script in the current working directory.
```{r setup environment}
source("environment.R")
```

```{r}
source_rmd("production.Rmd")
```

```{r eval=FALSE, include=FALSE}
print(production)
print(residual)
```

Calculate the summary statistics for each site and year. This method is slightly different from the previous method, instead of grouping by year, each site-year (e.g., Boggy 2017) has summary statistics generated and stored into a object. Then those objects are bound together into a data frame.

```{r eval=FALSE, include=FALSE}
residual_stats <- NULL

BGW17 <- residual %>% 
  dplyr::filter(Site == "Boggy" & Year == 2017) %>% 
  rstatix::get_summary_stats(lb_acre, type = "common")
BGW18 <- residual %>% 
  dplyr::filter(Site == "Boggy" & Year == 2018) %>% 
  rstatix::get_summary_stats(lb_acre, type = "common")
BGW19 <- residual %>% 
  dplyr::filter(Site == "Boggy" & Year == 2019) %>% 
  rstatix::get_summary_stats(lb_acre, type = "common")
WCS17 <- residual %>% 
  dplyr::filter(Site == "Wildcat" & Year == 2017) %>% 
  rstatix::get_summary_stats(lb_acre, type = "common")
WCS18 <- residual %>% 
  dplyr::filter(Site == "Wildcat" & Year == 2018) %>% 
  rstatix::get_summary_stats(lb_acre, type = "common")
WCS19 <- residual %>% 
  dplyr::filter(Site == "Wildcat" & Year == 2019) %>% 
  rstatix::get_summary_stats(lb_acre, type = "common")

residual_stats <- residual_stats %>% bind_rows(BGW17, BGW18, BGW19, WCS17, WCS18, WCS19)

# add the site names to the data frame 
residual_stats <- residual_stats %>% 
  add_column(site = c("BGW17", "BGW18", "BGW19", "WCS17", "WCS18", "WCS19"), .before = 1)

print(residual_stats)
```

```{r eval=FALSE, include=FALSE}
print(production_stats)
```

```{r eval=FALSE, include=FALSE}
residual_stats$min <- as.numeric(residual_stats$min) 
residual_stats$max <- as.numeric(residual_stats$max)
residual_stats$median <- as.numeric(residual_stats$median)
residual_stats$mean <- as.numeric(residual_stats$mean)

print(residual_stats)
```

## Heber

### 2021

```{r}
print(heber_production_stats_2021)
```

```{r}
heber_production_stats_2021 <- heber_production_stats_2021 %>% 
  dplyr::mutate(variable = "Production")
print(heber_production_stats_2021)
```

```{r}
print(heber_residuals_stats_2021)
```

```{r}
heber_residuals_stats_2021 <- heber_residuals_stats_2021 %>% 
  dplyr::mutate(variable = "Availability")
print(heber_residuals_stats_2021)
```

```{r}
heber_paired_plot_2021 <- bind_rows(heber_production_stats_2021, heber_residuals_stats_2021)
print(heber_paired_plot_2021)
```

```{r}
calc_utilization <- function(production, residual){
  utilization <- as.numeric(((production$mean - residual$mean) / production$mean) * 100)
  utilization <- dplyr::if_else(utilization < 0, 0, utilization, NA_real_)
  utilization <- tibble(perc_util = round(utilization, digits = 1),
                        site = production$Site)
}
```


```{r}
heber_utilization_2021 <- calc_utilization(heber_production_stats_2021,
                                           heber_residuals_stats_2021)
print(heber_utilization_2021)
```

```{r}
heber_paired_plot_2021$variable <- heber_paired_plot_2021 %>% 
  pull(variable) %>% 
  forcats::as_factor()
print(heber_paired_plot_2021)
```


```{r}
heber_paired_plot_2021$mean <- heber_paired_plot_2021$mean %>% as.numeric()
heber_paired_plot_2021$sd <- heber_paired_plot_2021$sd %>% as.numeric()
heber_paired_plot_2021$ci <- heber_paired_plot_2021$ci %>% as.numeric()
```


```{r}
excel_colors <- c(rep("#4472C4", 3), rep("#ED7D31", 3))
```


```{r}
ggplot(heber_paired_plot_2021, aes(fill = variable, y = mean, x = Site)) +
  geom_col(width = 0.7, position = position_dodge(0.7)) +
  labs(title = expression(atop("Heber Wild Horse Territory", 
                               paste("Paired Plot"))), 
       subtitle = "2021") +
  ylab(expression(paste("Pounds ", "Acre"^"-1", " ± 95% CI"))) + 
  xlab("Percent Utilization") +
  scale_y_continuous(limits = c(-200,3200), 
                     breaks = seq(0, 3000, by = 500)) +
  geom_errorbar(aes(ymin = (mean - ci), ymax = (mean + ci)), 
                position = position_dodge(0.7), width = 0.25) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 10, l = 0)),
        axis.ticks.x.bottom = element_blank()) +
  annotate(geom = "text", 
           x = 1, 
           y = heber_paired_plot_2021$mean[1] + heber_paired_plot_2021$ci[1] + 300, 
           label = paste0(heber_utilization_2021$perc_util[1], "%")) +
  annotate(geom = "text", 
           x = 2, 
           y = heber_paired_plot_2021$mean[2] + heber_paired_plot_2021$ci[2] + 300,  
           label = paste0(heber_utilization_2021$perc_util[2], "%")) +
  annotate(geom = "text", 
           x = 3, 
           y = heber_paired_plot_2021$mean[3] + heber_paired_plot_2021$ci[3] + 300, 
           label = paste0(heber_utilization_2021$perc_util[3], "%")) +
  annotate(geom = "text", 
           x = 4, 
           y = heber_paired_plot_2021$mean[4] + heber_paired_plot_2021$ci[4] + 300, 
           label = paste0(heber_utilization_2021$perc_util[4], "%")) +
  annotate(geom = "text", 
           x = 5, 
           y = heber_paired_plot_2021$mean[5] + heber_paired_plot_2021$ci[5] + 300,  
           label = paste0(heber_utilization_2021$perc_util[5], "%"))
ggsave(filename = "2021-heber-utilization.jpg",
       path = file.path("figures", "utilization", "heber"),
       width = 9,
       height = 6,
       units = "in")
```


```{r}
ggplot(veg_data, aes(fill = Type, y = mean, x = site)) +
  geom_col(width = 0.7, position = position_dodge(0.7)) +
  labs(title = "White Mountains Vegetation Utilization", subtitle = "2017-2019") +
  ylab(expression(paste("Pounds ", "Acre"^"-1", " ± SE"))) + 
  xlab("Percent Utilization") +
  scale_y_continuous(limits = c(-500,6000), breaks = c(seq(1000, 5000, by = 1000))) +
  geom_errorbar(aes(ymin = (mean-se), ymax = (mean+se)), position = position_dodge(0.7), width = 0.25) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.x = element_text(margin = margin(t = 5, r = 0, b = 10, l = 0)),
        axis.ticks.x.bottom = element_blank()) +
  annotate(geom = "text", x = 1, y = -500, label = paste0(utilization[1], "%")) +
  annotate(geom = "text", x = 2, y = -500, label = paste0(utilization[2], "%")) +
  annotate(geom = "text", x = 3, y = -500, label = paste0(utilization[3], "%")) +
  annotate(geom = "text", x = 4, y = -500, label = paste0(utilization[4], "%")) +
  annotate(geom = "text", x = 5, y = -500, label = paste0(utilization[5], "%")) +
  annotate(geom = "text", x = 6, y = -500, label = paste0(utilization[6], "%"))
  
ggsave("Utilization-Across-Year-Comparison-Values-Under-Bars-Adjust-Center.jpg", 
    path = paste0(getwd(),"/figures", "/utilization"))
```

