---
title: "Figures"
author: "Andrew Antaya"
date: "June 24, 2019"
output: html_notebook
---

```{r}
# # Boggy Trail 2018 Counts
#  jpeg(filename = "figures/counts/BGT18_Counts_Small.jpeg",
#       width=3.2,
#       height=3.2,
#       units="in",
#       res=300)
#  ## bottom, left, top, right
#  par(mar=c(2, 2, 1, 2))
#  barplot(BGT18counts$freq,
#          col = c("#4472C4", "#ED7D31", "#FFC000"),
#          main = "Boggy Creek Trail 2018",
#          cex.main = 0.75,
#          cex.lab = 0.5,
#          cex.names = 0.75,
#          axes = FALSE,
# xlab = NA,
#          ylab = NA,
#          ylim = c(0, 10000),
#          las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
#  mtext("Counts", 2, las = 0 , cex = 0.66, padj = -3)
#  text(0.7, 2775, "2775", pos = 3, cex = 0.75)
#  text(1.9, 114, "114", pos = 3, cex = 0.75)
#  text(3.1, 344, "344", pos = 3, cex = 0.75)
#  axis(2, at = seq(0, 10000, by=500), cex.axis = .5, padj = 2)
#  dev.off()
```

# 
```{r}
# # Boggy West 2017 Counts
# jpeg(filename = "figures/counts/BGW17_Counts_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(2, 2, 1, 2))
# barplot(BGW17counts$freq,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Timelapse 2017",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 10000),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Counts", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 7686, "7686", pos = 3, cex = 0.75)
# text(1.9, 2095, "2095", pos = 3, cex = 0.75)
# text(3.1, 1942, "1942", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 10000, by=500), cex.axis = .5, padj = 2)
# dev.off()
```

# 
# 
```{r}
# # Boggy West 2018 Counts
# jpeg(filename = "figures/counts/BGW18_Counts_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(2, 2, 1, 2))
# barplot(BGW18counts$freq,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Timelapse 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 10000),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Counts", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 5135, "5135", pos = 3, cex = 0.75)
# text(1.9, 199, "199", pos = 3, cex = 0.75)
# text(3.1, 898, "898", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 10000, by=500), cex.axis = .5, padj = 2)
# dev.off()
```
# 
```{r}
# # Boggy Exclosure 2018 Counts
# jpeg(filename = "figures/counts/BGX18_Counts_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(2, 2, 1, 2))
# barplot(BGX18counts$freq,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Exclosure 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 10000),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Counts", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 0, "0", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 634, "634", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 10000, by=500), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# 
# 
```{r}
# # Wildcat Timelapse 2017 Counts
# jpeg(filename = "figures/counts/WCS17_Counts_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(2, 2, 1, 2))
# barplot(WCS17counts$freq,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Timelapse 2017",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 25000),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Counts", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 22906, "22906", pos = 3, cex = 0.75)
# text(1.9, 13317, "13317", pos = 3, cex = 0.75)
# text(3.1, 13486, "13486", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 25000, by=5000), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# 
# 
```{r}
# # Wildcat Timelapse 2018 Counts
# jpeg(filename = "figures/counts/WCS18_Counts_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(2, 2, 1, 2))
# barplot(WCS18counts$freq,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Timelapse 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 25000),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Counts", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 9400, "9400", pos = 3, cex = 0.75)
# text(1.9, 6544, "6544", pos = 3, cex = 0.75)
# text(3.1, 1817, "1817", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 25000, by=5000), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# 
# 
```{r}
# # Wildcat Trail 2018 Counts
# jpeg(filename = "figures/counts/WCT18_Counts_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(2, 2, 1, 2))
# barplot(WCT18counts$freq,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Trail 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 25000),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Counts", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 2071, "2071", pos = 3, cex = 0.75)
# text(1.9, 342, "342", pos = 3, cex = 0.75)
# text(3.1, 398, "398", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 25000, by=5000), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# 
# 
```{r}
# # Wildcat Exclosure 2018 Counts
# jpeg(filename = "figures/counts/WCX18_Counts_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(2, 2, 1, 2))
# barplot(WCX18counts$freq,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Exclosure 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 25000),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Counts", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 494, "494", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 2110, "2110", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 25000, by=5000), cex.axis = .5, padj = 2)
# dev.off()
# 
```

```{r}
# Area 51 Counts 2019
 jpeg(filename = "figures/counts/A51_2019_Small.jpeg",
      width=3.2,
      height=3.2,
      units="in",
      res=300)
 ## bottom, left, top, right
 par(mar=c(2, 2, 1, 2))
 barplot(A51_2019counts$freq,
         col = c("#4472C4", "#ED7D31", "#FFC000"),
         main = "Area Fifty One Counts 2019",
         cex.main = 0.75,
         cex.lab = 0.5,
         cex.names = 0.75,
         axes = FALSE,
xlab = NA,
         ylab = NA,
         ylim = c(0, 10000),
         las = 0)
axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
 mtext("Counts", 2, las = 0 , cex = 0.66, padj = -3)
 text(0.7, 2775, "2714", pos = 3, cex = 0.75)
 text(1.9, 2200, "2186", pos = 3, cex = 0.75)
 text(3.1, 10, "7", pos = 3, cex = 0.75)
 axis(2, at = seq(0, 10000, by=500), cex.axis = .5, padj = 2)
 dev.off()
```

```{r}
# Area 51 Counts 2020
 jpeg(filename = "figures/counts/A51_2020_Small.jpeg",
      width=3.2,
      height=3.2,
      units="in",
      res=300)
 ## bottom, left, top, right
 par(mar=c(2, 2, 1, 2))
 barplot(A51_2020counts$freq,
         col = c("#4472C4", "#ED7D31", "#FFC000"),
         main = "Area Fifty One Counts 2020",
         cex.main = 0.75,
         cex.lab = 0.5,
         cex.names = 0.75,
         axes = FALSE,
xlab = NA,
         ylab = NA,
         ylim = c(0, 10000),
         las = 0)
axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
 mtext("Counts", 2, las = 0 , cex = 0.66, padj = -3)
 text(0.7, 4500, "4304", pos = 3, cex = 0.75)
 text(1.9, 1100, "1069", pos = 3, cex = 0.75)
 text(3.1, 25, "17", pos = 3, cex = 0.75)
 axis(2, at = seq(0, 10000, by=500), cex.axis = .5, padj = 2)
 dev.off()
```


# 
# ### Number of Groups
# 
# 
```{r}
# # Boggy Trail 2018 Groups
# jpeg(filename = "figures/BGT18_Groups_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(2, 2, 2, 2))
# barplot(BGT18grouptotals$groups,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Trail 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 250),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Groups", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 129, "129", pos = 3, cex = 0.75)
# text(1.9, 13, "13", pos = 3, cex = 0.75)
# text(3.1, 36, "36", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 250, by=50), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# 
# 
```{r}
# # Boggy West 2017 Groups
# jpeg(filename = "figures/BGW17_Groups_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# par(mar=c(2, 2, 2, 2))
# barplot(BGW17grouptotals$groups,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main ="Boggy Creek Timelapse 2017",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 250),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Groups", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 119, "119", pos = 3, cex = 0.75)
# text(1.9, 43, "43", pos = 3, cex = 0.75)
# text(3.1, 72, "72", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 250, by=50), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# 
# 
```{r}
# # Boggy West 2018 Groups
# jpeg(filename = "figures/BGW18_Groups_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# par(mar=c(2, 2, 2, 2))
# barplot(BGW18grouptotals$groups,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main ="Boggy Creek Timelapse 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 250),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Groups", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 74, "74", pos = 3, cex = 0.75)
# text(1.9, 11, "11", pos = 3, cex = 0.75)
# text(3.1, 57, "57", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 250, by=50), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# 
# 
```{r}
# # Boggy Exclosure 2018 Groups
# jpeg(filename = "figures/BGX18_Groups_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# par(mar=c(2, 2, 2, 2))
# barplot(BGX18grouptotals$groups,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main ="Boggy Creek Exclosure 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 250),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Groups", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 0, "0", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 16, "16", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 250, by=50), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# 
# 
```{r}
# # Wildcat South 2017 Groups
# jpeg(filename = "figures/WCS17_Groups_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# par(mar=c(2, 2, 2, 2))
# barplot(WCS17grouptotals$groups,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main ="Wildcat Creek Timelapse 2017",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 250),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Groups", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 218, "218", pos = 3, cex = 0.75)
# text(1.9, 73, "73", pos = 3, cex = 0.75)
# text(3.1, 135, "135", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 250, by=50), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# 
# 
```{r}
# # Wildcat South 2018 Groups
# jpeg(filename = "figures/WCS18_Groups_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# par(mar=c(2, 2, 2, 2))
# barplot(WCS18grouptotals$groups,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main ="Wildcat Creek Timelapse 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 250),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Groups", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 97, "97", pos = 3, cex = 0.75)
# text(1.9, 23, "23", pos = 3, cex = 0.75)
# text(3.1, 73, "73", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 250, by=50), cex.axis = .5, padj = 2)
# dev.off()
# 
# 
```
# 
# 
```{r}
# # Wildcat Trail 2018 Groups
# jpeg(filename = "figures/WCT18_Groups_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# par(mar=c(2, 2, 2, 2))
# barplot(WCT18grouptotals$groups,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main ="Wildcat Creek Trail 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 250),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Groups", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 91, "91", pos = 3, cex = 0.75)
# text(1.9, 16, "16", pos = 3, cex = 0.75)
# text(3.1, 52, "52", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 250, by=50), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# 
# 
```{r}
# # Wildcat Exclosure 2018 Groups
# jpeg(filename = "figures/WCX18_Groups_Small.jpeg",
#      width=3.2,
#      height=3.2,
#      units="in",
#      res=300)
# par(mar=c(2, 2, 2, 2))
# barplot(WCX18grouptotals$groups,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main ="Wildcat Creek Exclosure 2018",
#         cex.main = 0.75,
#         cex.lab = 0.5,
#         cex.names = 0.75,
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0, 250),
#         las = 0)
# axis(1, at = seq(0.7, 3.1, by=1.2), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Groups", 2, las = 0 , cex = 0.66, padj = -3)
# text(0.7, 47, "47", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 47, "47", pos = 3, cex = 0.75)
# axis(2, at = seq(0, 250, by=50), cex.axis = .5, padj = 2)
# dev.off()
# 
```
# ### Site Use by Time of Day
# 
```{r}
# ### Boggy Trail 2018 Site Use by Time of Day 
# jpeg(filename = "figures/timeofday/BGT18_Time_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 2, 2))
# matplot(c(0:23), BGT18time, 
#         type = c("o"),
#         main = "Boggy Creek Trail 2018",
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0,2000),
#         pch = 16,
#         lty = 1,
#         lwd = 2,
#         col = c("#4472C4", "#ED7D31", "#FFC000"))
# legend("topleft", 
#        legend = c("Horses", "Cattle", "Elk"),
#        cex = 1.25,
#        col = c("#4472C4", "#ED7D31", "#FFC000"), 
#        pch = 16)
# axis(2, at = seq(0, 2000, by=100), labels = c(seq(0, 2000, by=100)), cex.axis = 0.75)
# axis(1, at = 0:23, labels = (hrs), las = 2, cex.axis = 0.75)
# mtext("Time of Day (24hrs)", 1, las = 0 , cex = 1, padj = 6)
# mtext("Count", 2, las = 0 , cex = 1, padj = -3)
# dev.off()
# 
```
# 
# 
```{r}
# ### Boggy West Timelapse 2017 Site Use by Time of Day 
# jpeg(filename = "figures/timeofday/BGW17_Time_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 2, 2))
# matplot(c(0:23), BGW17time, 
#         type = c("o"),
#         main = "Boggy Creek Timelapse 2017",
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0,2000),
#         pch = 16,
#         lty = 1,
#         lwd = 2,
#         col = c("#4472C4", "#ED7D31", "#FFC000"))
# legend("topleft", 
#        legend = c("Horses", "Cattle", "Elk"),
#        cex = 1.25,
#        col = c("#4472C4", "#ED7D31", "#FFC000"), 
#        pch = 16)
# axis(2, at = seq(0, 2000, by=100), labels = c(seq(0, 2000, by=100)), cex.axis = 0.75)
# axis(1, at = 0:23, labels = (hrs), las = 2, cex.axis = 0.75)
# mtext("Time of Day (24hrs)", 1, las = 0 , cex = 1, padj = 6)
# mtext("Count", 2, las = 0 , cex = 1, padj = -3)
# dev.off()
# 
```
# 
# 
```{r}
# ### Boggy West Timelapse 2018 Site Use by Time of Day 
# jpeg(filename = "figures/timeofday/BGW18_Time_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 2, 2))
# matplot(c(0:23), BGW18time, 
#         type = c("o"),
#         main = "Boggy Creek Timelapse 2018",
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0,2000),
#         pch = 16,
#         lty = 1,
#         lwd = 2,
#         col = c("#4472C4", "#ED7D31", "#FFC000"))
# legend("topleft", 
#        legend = c("Horses", "Cattle", "Elk"),
#        cex = 1.25,
#        col = c("#4472C4", "#ED7D31", "#FFC000"), 
#        pch = 16)
# axis(2, at = seq(0, 2000, by=100), labels = c(seq(0, 2000, by=100)), cex.axis = 0.75)
# axis(1, at = 0:23, labels = (hrs), las = 2, cex.axis = 0.75)
# mtext("Time of Day (24hrs)", 1, las = 0 , cex = 1, padj = 6)
# mtext("Count", 2, las = 0 , cex = 1, padj = -3)
# dev.off()
# 
```
# 
# 
```{r}
# ### Boggy Exclosure 2018 Site Use by Time of Day 
# jpeg(filename = "figures/timeofday/BGX18_Time_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 2, 2))
# matplot(c(0:23), BGX18time, 
#         type = c("o"),
#         main = "Boggy Creek Exclosure 2018",
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0,2000),
#         pch = 16,
#         lty = 1,
#         lwd = 2,
#         col = c("#4472C4", "#ED7D31", "#FFC000"))
# legend("topleft", 
#        legend = c("Horses", "Cattle", "Elk"),
#        cex = 1.25,
#        col = c("#4472C4", "#ED7D31", "#FFC000"), 
#        pch = 16)
# axis(2, at = seq(0, 2000, by=100), labels = c(seq(0, 2000, by=100)), cex.axis = 0.75)
# axis(1, at = 0:23, labels = (hrs), las = 2, cex.axis = 0.75)
# mtext("Time of Day (24hrs)", 1, las = 0 , cex = 1, padj = 6)
# mtext("Count", 2, las = 0 , cex = 1, padj = -3)
# dev.off()
# 
```
# 
# 
```{r}
# ### Wildcat Timelapse 2017 Site Use by Time of Day 
# jpeg(filename = "figures/timeofday/WCS17_Time_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 2, 2))
# matplot(c(0:23), WCS17time, 
#         type = c("o"),
#         main = "Wildcat Creek Timelapse 2017",
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0,4500),
#         pch = 16,
#         lty = 1,
#         lwd = 2,
#         col = c("#4472C4", "#ED7D31", "#FFC000"))
# legend("topleft", 
#        legend = c("Horses", "Cattle", "Elk"),
#        cex = 1.25,
#        col = c("#4472C4", "#ED7D31", "#FFC000"), 
#        pch = 16)
# axis(2, at = seq(0, 4500, by=500), labels = c(seq(0, 4500, by=500)), cex.axis = 0.75)
# axis(1, at = 0:23, labels = (hrs), las = 2, cex.axis = 0.75)
# mtext("Time of Day (24hrs)", 1, las = 0 , cex = 1, padj = 6)
# mtext("Count", 2, las = 0 , cex = 1, padj = -3)
# dev.off()
# 
```

```{r}
# ### Wildcat Timelapse 2018 Site Use by Time of Day 
# jpeg(filename = "figures/timeofday/WCS18_Time_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 2, 2))
# matplot(c(0:23), WCS18time, 
#         type = c("o"),
#         main = "Wildcat Creek Timelapse 2018",
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0,2000),
#         pch = 16,
#         lty = 1,
#         lwd = 2,
#         col = c("#4472C4", "#ED7D31", "#FFC000"))
# legend("topleft", 
#        legend = c("Horses", "Cattle", "Elk"),
#        cex = 1.25,
#        col = c("#4472C4", "#ED7D31", "#FFC000"), 
#        pch = 16)
# axis(2, at = seq(0, 2000, by=100), labels = c(seq(0, 2000, by=100)), cex.axis = 0.75)
# axis(1, at = 0:23, labels = (hrs), las = 2, cex.axis = 0.75)
# mtext("Time of Day (24hrs)", 1, las = 0 , cex = 1, padj = 6)
# mtext("Count", 2, las = 0 , cex = 1, padj = -3)
# dev.off()
# 
```
# 
# 
```{r}
# ### Wildcat Trail 2018 Site Use by Time of Day 
# jpeg(filename = "figures/timeofday/WCT18_Time_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 2, 2))
# matplot(c(0:23), WCT18time, 
#         type = c("o"),
#         main = "Wildcat Creek Trail 2018",
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0,2000),
#         pch = 16,
#         lty = 1,
#         lwd = 2,
#         col = c("#4472C4", "#ED7D31", "#FFC000"))
# legend("topleft", 
#        legend = c("Horses", "Cattle", "Elk"),
#        cex = 1.25,
#        col = c("#4472C4", "#ED7D31", "#FFC000"), 
#        pch = 16)
# axis(2, at = seq(0, 2000, by=100), labels = c(seq(0, 2000, by=100)), cex.axis = 0.75)
# axis(1, at = 0:23, labels = (hrs), las = 2, cex.axis = 0.75)
# mtext("Time of Day (24hrs)", 1, las = 0 , cex = 1, padj = 6)
# mtext("Count", 2, las = 0 , cex = 1, padj = -3)
# dev.off()
# 
```
# 
# 
```{r}
# ### Wildcat Exclosure 2018 Site Use by Time of Day 
# jpeg(filename = "figures/timeofday/WCX18_Time_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 2, 2))
# matplot(c(0:23), WCX18time, 
#         type = c("o"),
#         main = "Wildcat Creek Exclosure 2018",
#         axes = FALSE,
#         xlab = NA,
#         ylab = NA,
#         ylim = c(0,2000),
#         pch = 16,
#         lty = 1,
#         lwd = 2,
#         col = c("#4472C4", "#ED7D31", "#FFC000"))
# legend("topleft", 
#        legend = c("Horses", "Cattle", "Elk"),
#        cex = 1.25,
#        col = c("#4472C4", "#ED7D31", "#FFC000"), 
#        pch = 16)
# axis(2, at = seq(0, 2000, by=100), labels = c(seq(0, 2000, by=100)), cex.axis = 0.75)
# axis(1, at = 0:23, labels = (hrs), las = 2, cex.axis = 0.75)
# mtext("Time of Day (24hrs)", 1, las = 0 , cex = 1, padj = 6)
# mtext("Count", 2, las = 0 , cex = 1, padj = -3)
# dev.off()
# 
```
# ### Number of Groups by Monsoonal Period
# 
```{r}
# jpeg(filename = "figures/monsoon/BGW17_Monsoon_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 4, 2))
# barplot(BGW17groups, 
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Timelapse 2017",
#         sub = "Number of Groups by Monsoonal Period",
#         ylim = c(0,150),
#         axes = FALSE,
#         border = "black",
#         beside = TRUE,
#         legend = rownames(BGW17groups),
#         font.axis = 3,
#         font.lab = 2)
# axis(2, at = seq(0, 150, by=10), labels = c(seq(0, 150, by=10)), cex.axis = 0.75, las = 2)
# text(1.5, 8, "8", pos = 3, cex = 0.75)
# text(2.5, 2, "2", pos = 3, cex = 0.75)
# text(3.5, 12, "12", pos = 3, cex = 0.75)
# text(5.5, 43, "43", pos = 3, cex = 0.75)
# text(6.5, 10, "10", pos = 3, cex = 0.75)
# text(7.5, 22, "22", pos = 3, cex = 0.75)
# text(9.5, 68, "68", pos = 3, cex = 0.75)
# text(10.5, 31, "31", pos = 3, cex = 0.75)
# text(11.5, 38, "38", pos = 3, cex = 0.75)
# dev.off()
# 
```
# 
# 
```{r}
# jpeg(filename = "figures/monsoon/BGW18_Monsoon_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 4, 2))
# barplot(BGW18groups, 
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Timelapse 2018",
#         sub = "Number of Groups by Monsoonal Period",
#         ylim = c(0,150),
#         axes = FALSE,
#         border = "black",
#         beside = TRUE,
#         legend = rownames(BGW18groups),
#         font.axis = 3,
#         font.lab = 2)
# axis(2, at = seq(0, 150, by=10), labels = c(seq(0, 150, by=10)), cex.axis = 0.75, las = 2)
# text(1.5, 21, "21", pos = 3, cex = 0.75)
# text(2.5, 0, "0", pos = 3, cex = 0.75)
# text(3.5, 39, "39", pos = 3, cex = 0.75)
# text(5.5, 24, "24", pos = 3, cex = 0.75)
# text(6.5, 1, "1", pos = 3, cex = 0.75)
# text(7.5, 7, "7", pos = 3, cex = 0.75)
# text(9.5, 29, "29", pos = 3, cex = 0.75)
# text(10.5, 10, "10", pos = 3, cex = 0.75)
# text(11.5, 11, "11", pos = 3, cex = 0.75)
# dev.off()
# 
```
# 
# 
```{r}
# jpeg(filename = "figures/monsoon/WCS17_Monsoon_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 4, 2))
# barplot(WCS17groups, 
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Timelapse 2017",
#         sub = "Number of Groups by Monsoonal Period",
#         ylim = c(0,150),
#         axes = FALSE,
#         border = "black",
#         beside = TRUE,
#         legend = rownames(WCS17groups),
#         font.axis = 3,
#         font.lab = 2)
# axis(2, at = seq(0, 150, by=10), labels = c(seq(0, 150, by=10)), cex.axis = 0.75, las = 2)
# text(1.5, 131, "131", pos = 3, cex = 0.75)
# text(2.5, 21, "21", pos = 3, cex = 0.75)
# text(3.5, 52, "52", pos = 3, cex = 0.75)
# text(5.5, 39, "39", pos = 3, cex = 0.75)
# text(6.5, 26, "26", pos = 3, cex = 0.75)
# text(7.5, 39, "39", pos = 3, cex = 0.75)
# text(9.5, 48, "48", pos = 3, cex = 0.75)
# text(10.5, 26, "26", pos = 3, cex = 0.75)
# text(11.5, 44, "44", pos = 3, cex = 0.75)
# dev.off()
# 
```
# 
# 
```{r}
# jpeg(filename = "figures/monsoon/WCS18_Monsoon_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# par(mar=c(5, 4, 4, 2))
# barplot(WCS18groups, 
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Timelapse 2018",
#         sub = "Number of Groups by Monsoonal Period",
#         ylim = c(0,150),
#         axes = FALSE,
#         border = "black",
#         beside = TRUE,
#         legend = rownames(WCS18groups),
#         font.axis = 3,
#         font.lab = 2)
# axis(2, at = seq(0, 150, by=10), labels = c(seq(0, 150, by=10)), cex.axis = 0.75, las = 2)
# text(1.5, 77, "77", pos = 3, cex = 0.75)
# text(2.5, 0, "0", pos = 3, cex = 0.75)
# text(3.5, 41, "41", pos = 3, cex = 0.75)
# text(5.5, 3, "3", pos = 3, cex = 0.75)
# text(6.5, 0, "0", pos = 3, cex = 0.75)
# text(7.5, 0, "0", pos = 3, cex = 0.75)
# text(9.5, 17, "17", pos = 3, cex = 0.75)
# text(10.5, 23, "23", pos = 3, cex = 0.75)
# text(11.5, 32, "32", pos = 3, cex = 0.75)
# dev.off()
# ```
# ### Duration Figures
# #### Boggy Creek Trail Duration 2018
# 
```{r}
# jpeg(filename = "figures/duration/BGT18_Duration_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# barplot(BGT18duration$freq,
#         main = "Boggy Creek Trail 2018",
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         axes = FALSE,
#         ylab = "Total Time Spent at Site (mins)",
#         ylim = c(0,1500),
#         xlab = NA)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# axis(2, at = seq(0, 1500, by=100), labels = c(seq(0, 1500, by=100)), cex.axis = 0.75, las = 2)
# text(0.7, 499, "499", pos = 3, cex = 0.75)
# text(1.9, 22, "22", pos = 3, cex = 0.75)
# text(3.1, 85, "85", pos = 3, cex = 0.75)
# dev.off()
# 
```
# #### Boggy Creek Timelapse Duration 2017
# 
```{r}
# jpeg(filename = "figures/duration/BGW17_Duration_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# barplot(BGW17duration$freq,
#         main = "Boggy Creek Timelapse 2017",
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         axes = FALSE,
#         ylab = "Total Time Spent at Site (mins)",
#         ylim = c(0,1500),
#         xlab = NA)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# axis(2, at = seq(0, 1500, by=100), labels = c(seq(0, 1500, by=100)), cex.axis = 0.75, las = 2)
# text(0.7, 1320, "1320", pos = 3, cex = 0.75)
# text(1.9, 749, "749", pos = 3, cex = 0.75)
# text(3.1, 540, "540", pos = 3, cex = 0.75)
# dev.off()
# 
```
# #### Boggy Creek Timelapse Duration 2018
# 
```{r}
# jpeg(filename = "figures/duration/BGW18_Duration_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# barplot(BGW18duration$freq,
#         main = "Boggy Creek Timelapse 2018",
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         axes = FALSE,
#         ylab = "Total Time Spent at Site (mins)",
#         ylim = c(0,1500),
#         xlab = NA)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# axis(2, at = seq(0, 1500, by=100), labels = c(seq(0, 1500, by=100)), cex.axis = 0.75, las = 2)
# text(0.7, 899, "899", pos = 3, cex = 0.75)
# text(1.9, 89, "89", pos = 3, cex = 0.75)
# text(3.1, 347, "347", pos = 3, cex = 0.75)
# dev.off()
# 
```
# #### Boggy Creek Exclosure Duration 2018
# 
```{r}
# jpeg(filename = "figures/duration/BGX18_Duration_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# barplot(BGX18duration$freq,
#         main = "Boggy Creek Exclosure 2018",
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         axes = FALSE,
#         ylab = "Total Time Spent at Site (mins)",
#         ylim = c(0,1500),
#         xlab = NA)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# axis(2, at = seq(0, 1500, by=100), labels = c(seq(0, 1500, by=100)), cex.axis = 0.75, las = 2)
# text(0.7, 0, "0", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 299, "299", pos = 3, cex = 0.75)
# dev.off()
# ```
# #### Wildcat Creek Timelapse Duration 2017
# ```{r}
# jpeg(filename = "figures/duration/WCS17_Duration_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# barplot(WCS17duration$freq,
#         main = "Wildcat Creek Timelapse 2017",
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         axes = FALSE,
#         ylab = "Total Time Spent at Site (mins)",
#         ylim = c(0,6500),
#         xlab = NA)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# axis(2, at = seq(0, 6500, by=500), labels = c(seq(0, 6500, by=500)), cex.axis = 0.75, las = 2)
# text(0.7, 5903, "5903", pos = 3, cex = 0.75)
# text(1.9, 2975, "2975", pos = 3, cex = 0.75)
# text(3.1, 2287, "2287", pos = 3, cex = 0.75)
# dev.off()
# 
```
# #### Wildcat Creek Timelapse Duration 2018
# 
```{r}
# jpeg(filename = "figures/duration/WCS18_Duration_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# barplot(WCS18duration$freq,
#         main = "Wildcat Creek Timelapse 2018",
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         axes = FALSE,
#         ylab = "Total Time Spent at Site (mins)",
#         ylim = c(0,6500),
#         xlab = NA)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# axis(2, at = seq(0, 6500, by=500), labels = c(seq(0, 6500, by=500)), cex.axis = 0.75, las = 2)
# text(0.7, 3172, "3172", pos = 3, cex = 0.75)
# text(1.9, 1382, "1382", pos = 3, cex = 0.75)
# text(3.1, 802, "802", pos = 3, cex = 0.75)
# dev.off()
# 
```
# #### Wildcat Creek Trail Duration 2018
# 
```{r}
# jpeg(filename = "figures/duration/WCT18_Duration_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# barplot(WCT18duration$freq,
#         main = "Wildcat Creek Trail 2018",
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         axes = FALSE,
#         ylab = "Total Time Spent at Site (mins)",
#         ylim = c(0,6500),
#         xlab = NA)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# axis(2, at = seq(0, 6500, by=500), labels = c(seq(0, 6500, by=500)), cex.axis = 0.75, las = 2)
# text(0.7, 1112, "1112", pos = 3, cex = 0.75)
# text(1.9, 122, "122", pos = 3, cex = 0.75)
# text(3.1, 137, "137", pos = 3, cex = 0.75)
# dev.off()
# ```
# #### Wildcat Creek Exclosure Duration 2018
# ```{r}
# jpeg(filename = "figures/duration/WCX18_Duration_Small.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# ## bottom, left, top, right
# barplot(WCX18duration$freq,
#         main = "Wildcat Creek Exclosure 2018",
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         axes = FALSE,
#         ylab = "Total Time Spent at Site (mins)",
#         ylim = c(0,6500),
#         xlab = NA)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# axis(2, at = seq(0, 6500, by=500), labels = c(seq(0, 6500, by=500)), cex.axis = 0.75, las = 2)
# text(0.7, 376, "376", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 955, "955", pos = 3, cex = 0.75)
# dev.off()
# ```
# ***
# ### Group Size Figures
# #### Boggy Creek Trail 2018
# ```{r}
# jpeg(filename = "figures/groupsize/BGT18_GroupSize.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGT18groupsize$avg,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Trail 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 10))
# axis(2,at=c(seq(0,10,1)), labels=c(seq(0,10,1)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# segments(0.7, BGT18groupsize$avg[1] - BGT18groupsize$se[1], 0.7, 
#          BGT18groupsize$avg[1] + BGT18groupsize$se[1], lwd = 1)
# arrows(0.7, BGT18groupsize$avg[1] - BGT18groupsize$se[1], 0.7,
#       BGT18groupsize$avg[1] + BGT18groupsize$se[1], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(1.9, BGT18groupsize$avg[2] - BGT18groupsize$se[2], 1.9, 
#          BGT18groupsize$avg[2] + BGT18groupsize$se[2], lwd = 1)
# arrows(1.9, BGT18groupsize$avg[2] - BGT18groupsize$se[2], 1.9,
#       BGT18groupsize$avg[2] + BGT18groupsize$se[2], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(3.1, BGT18groupsize$avg[3] - BGT18groupsize$se[3], 3.1, 
#          BGT18groupsize$avg[3] + BGT18groupsize$se[3], lwd = 1)
# arrows(3.1, BGT18groupsize$avg[3] - BGT18groupsize$se[3], 3.1,
#       BGT18groupsize$avg[3] + BGT18groupsize$se[3], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# mtext(expression(paste("Number of Individuals", " ± SE")), 2, las = 0 , cex = 1, padj = -3)
# mtext("Average Group Size", 3, las = 0 , cex = 1, padj = 3)
# text(0.7, 4.5, "4", pos = 3, cex = 0.75)
# text(1.9, 2.5, "2", pos = 3, cex = 0.75)
# text(3.1, 2.5, "2", pos = 3, cex = 0.75)
# dev.off()
```

***
### 
```{r}
# jpeg(filename = "figures/groupsize/BGW17_GroupSize.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGW17groupsize$avg,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Timelapse 2017",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 10))
# axis(2,at=c(seq(0,10,1)), labels=c(seq(0,10,1)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# segments(0.7, BGW17groupsize$avg[1] - BGW17groupsize$se[1], 0.7, 
#          BGW17groupsize$avg[1] + BGW17groupsize$se[1], lwd = 1)
# arrows(0.7, BGW17groupsize$avg[1] - BGW17groupsize$se[1], 0.7,
#       BGW17groupsize$avg[1] + BGW17groupsize$se[1], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(1.9, BGW17groupsize$avg[2] - BGW17groupsize$se[2], 1.9, 
#          BGW17groupsize$avg[2] + BGW17groupsize$se[2], lwd = 1)
# arrows(1.9, BGW17groupsize$avg[2] - BGW17groupsize$se[2], 1.9,
#       BGW17groupsize$avg[2] + BGW17groupsize$se[2], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(3.1, BGW17groupsize$avg[3] - BGW17groupsize$se[3], 3.1, 
#          BGW17groupsize$avg[3] + BGW17groupsize$se[3], lwd = 1)
# arrows(3.1, BGW17groupsize$avg[3] - BGW17groupsize$se[3], 3.1,
#       BGW17groupsize$avg[3] + BGW17groupsize$se[3], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# mtext(expression(paste("Number of Individuals", " ± SE")), 2, las = 0 , cex = 1, padj = -3)
# mtext("Average Group Size", 3, las = 0 , cex = 1, padj = 3)
# text(0.7, 6.5, "6", pos = 3, cex = 0.75)
# text(1.9, 4.5, "4", pos = 3, cex = 0.75)
# text(3.1, 4.5, "4", pos = 3, cex = 0.75)
# dev.off()
```
***
### 
```{r}
# jpeg(filename = "figures/groupsize/BGW18_GroupSize.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGW18groupsize$avg,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Timelapse 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 10))
# axis(2,at=c(seq(0,10,1)), labels=c(seq(0,10,1)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# segments(0.7, BGW18groupsize$avg[1] - BGW18groupsize$se[1], 0.7, 
#          BGW18groupsize$avg[1] + BGW18groupsize$se[1], lwd = 1)
# arrows(0.7, BGW18groupsize$avg[1] - BGW18groupsize$se[1], 0.7,
#       BGW18groupsize$avg[1] + BGW18groupsize$se[1], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(1.9, BGW18groupsize$avg[2] - BGW18groupsize$se[2], 1.9, 
#          BGW18groupsize$avg[2] + BGW18groupsize$se[2], lwd = 1)
# arrows(1.9, BGW18groupsize$avg[2] - BGW18groupsize$se[2], 1.9,
#       BGW18groupsize$avg[2] + BGW18groupsize$se[2], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(3.1, BGW18groupsize$avg[3] - BGW18groupsize$se[3], 3.1, 
#          BGW18groupsize$avg[3] + BGW18groupsize$se[3], lwd = 1)
# arrows(3.1, BGW18groupsize$avg[3] - BGW18groupsize$se[3], 3.1,
#       BGW18groupsize$avg[3] + BGW18groupsize$se[3], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# mtext(expression(paste("Number of Individuals", " ± SE")), 2, las = 0 , cex = 1, padj = -3)
# mtext("Average Group Size", 3, las = 0 , cex = 1, padj = 3)
# text(0.7, 5.5, "5", pos = 3, cex = 0.75)
# text(1.9, 2.5, "2", pos = 3, cex = 0.75)
# text(3.1, 2.5, "2", pos = 3, cex = 0.75)
# dev.off()
```
***
### 
```{r}
# jpeg(filename = "figures/groupsize/BGX18_GroupSize.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGX18groupsize$avg,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Exclosure 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 10))
# axis(2,at=c(seq(0,10,1)), labels=c(seq(0,10,1)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# segments(0.7, BGX18groupsize$avg[1] - BGX18groupsize$se[1], 0.7, 
#          BGX18groupsize$avg[1] + BGX18groupsize$se[1], lwd = 1)
# arrows(0.7, BGX18groupsize$avg[1] - BGX18groupsize$se[1], 0.7,
#       BGX18groupsize$avg[1] + BGX18groupsize$se[1], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(1.9, BGX18groupsize$avg[2] - BGX18groupsize$se[2], 1.9, 
#          BGX18groupsize$avg[2] + BGX18groupsize$se[2], lwd = 1)
# arrows(1.9, BGX18groupsize$avg[2] - BGX18groupsize$se[2], 1.9,
#       BGX18groupsize$avg[2] + BGX18groupsize$se[2], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(3.1, BGX18groupsize$avg[3] - BGX18groupsize$se[3], 3.1, 
#          BGX18groupsize$avg[3] + BGX18groupsize$se[3], lwd = 1)
# arrows(3.1, BGX18groupsize$avg[3] - BGX18groupsize$se[3], 3.1,
#       BGX18groupsize$avg[3] + BGX18groupsize$se[3], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# mtext(expression(paste("Number of Individuals", " ± SE")), 2, las = 0 , cex = 1, padj = -3)
# mtext("Average Group Size", 3, las = 0 , cex = 1, padj = 3)
# text(0.7, 0, "0", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 3.5, "3", pos = 3, cex = 0.75)
# dev.off()
```
***
### 
```{r}
# jpeg(filename = "figures/groupsize/WCS17_GroupSize.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCS17groupsize$avg,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Timelapse 2017",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 10))
# axis(2,at=c(seq(0,10,1)), labels=c(seq(0,10,1)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# segments(0.7, WCS17groupsize$avg[1] - WCS17groupsize$se[1], 0.7, 
#          WCS17groupsize$avg[1] + WCS17groupsize$se[1], lwd = 1)
# arrows(0.7, WCS17groupsize$avg[1] - WCS17groupsize$se[1], 0.7,
#       WCS17groupsize$avg[1] + WCS17groupsize$se[1], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(1.9, WCS17groupsize$avg[2] - WCS17groupsize$se[2], 1.9, 
#          WCS17groupsize$avg[2] + WCS17groupsize$se[2], lwd = 1)
# arrows(1.9, WCS17groupsize$avg[2] - WCS17groupsize$se[2], 1.9,
#       WCS17groupsize$avg[2] + WCS17groupsize$se[2], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(3.1, WCS17groupsize$avg[3] - WCS17groupsize$se[3], 3.1, 
#          WCS17groupsize$avg[3] + WCS17groupsize$se[3], lwd = 1)
# arrows(3.1, WCS17groupsize$avg[3] - WCS17groupsize$se[3], 3.1,
#       WCS17groupsize$avg[3] + WCS17groupsize$se[3], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# mtext(expression(paste("Number of Individuals", " ± SE")), 2, las = 0 , cex = 1, padj = -3)
# mtext("Average Group Size", 3, las = 0 , cex = 1, padj = 3)
# text(0.7, 4.5, "4", pos = 3, cex = 0.75)
# text(1.9, 6.5, "6", pos = 3, cex = 0.75)
# text(3.1, 4.5, "4", pos = 3, cex = 0.75)
# dev.off()
```
***
### 
```{r}
# jpeg(filename = "figures/groupsize/WCS18_GroupSize.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCS18groupsize$avg,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Timelapse 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 10))
# axis(2,at=c(seq(0,10,1)), labels=c(seq(0,10,1)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# segments(0.7, WCS18groupsize$avg[1] - WCS18groupsize$se[1], 0.7, 
#          WCS18groupsize$avg[1] + WCS18groupsize$se[1], lwd = 1)
# arrows(0.7, WCS18groupsize$avg[1] - WCS18groupsize$se[1], 0.7,
#       WCS18groupsize$avg[1] + WCS18groupsize$se[1], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(1.9, WCS18groupsize$avg[2] - WCS18groupsize$se[2], 1.9, 
#          WCS18groupsize$avg[2] + WCS18groupsize$se[2], lwd = 1)
# arrows(1.9, WCS18groupsize$avg[2] - WCS18groupsize$se[2], 1.9,
#       WCS18groupsize$avg[2] + WCS18groupsize$se[2], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(3.1, WCS18groupsize$avg[3] - WCS18groupsize$se[3], 3.1, 
#          WCS18groupsize$avg[3] + WCS18groupsize$se[3], lwd = 1)
# arrows(3.1, WCS18groupsize$avg[3] - WCS18groupsize$se[3], 3.1,
#       WCS18groupsize$avg[3] + WCS18groupsize$se[3], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# mtext(expression(paste("Number of Individuals", " ± SE")), 2, las = 0 , cex = 1, padj = -3)
# mtext("Average Group Size", 3, las = 0 , cex = 1, padj = 3)
# text(0.7, 4.5, "4", pos = 3, cex = 0.75)
# text(1.9, 7.75, "7", pos = 3, cex = 0.75)
# text(3.1, 2.5, "2", pos = 3, cex = 0.75)
# dev.off()
```
***
### 
```{r}
# jpeg(filename = "figures/groupsize/WCT18_GroupSize.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCT18groupsize$avg,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Trail 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 10))
# axis(2,at=c(seq(0,10,1)), labels=c(seq(0,10,1)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# segments(0.7, WCT18groupsize$avg[1] - WCT18groupsize$se[1], 0.7, 
#          WCT18groupsize$avg[1] + WCT18groupsize$se[1], lwd = 1)
# arrows(0.7, WCT18groupsize$avg[1] - WCT18groupsize$se[1], 0.7,
#       WCT18groupsize$avg[1] + WCT18groupsize$se[1], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(1.9, WCT18groupsize$avg[2] - WCT18groupsize$se[2], 1.9, 
#          WCT18groupsize$avg[2] + WCT18groupsize$se[2], lwd = 1)
# arrows(1.9, WCT18groupsize$avg[2] - WCT18groupsize$se[2], 1.9,
#       WCT18groupsize$avg[2] + WCT18groupsize$se[2], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(3.1, WCT18groupsize$avg[3] - WCT18groupsize$se[3], 3.1, 
#          WCT18groupsize$avg[3] + WCT18groupsize$se[3], lwd = 1)
# arrows(3.1, WCT18groupsize$avg[3] - WCT18groupsize$se[3], 3.1,
#       WCT18groupsize$avg[3] + WCT18groupsize$se[3], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# mtext(expression(paste("Number of Individuals", " ± SE")), 2, las = 0 , cex = 1, padj = -3)
# mtext("Average Group Size", 3, las = 0 , cex = 1, padj = 3)
# text(0.7, 2.5, "2", pos = 3, cex = 0.75)
# text(1.9, 3.5, "3", pos = 3, cex = 0.75)
# text(3.1, 2.5, "2", pos = 3, cex = 0.75)
# dev.off()
```
***
### 
```{r}
# jpeg(filename = "figures/groupsize/WCX18_GroupSize.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCX18groupsize$avg,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Exclosure 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 10))
# axis(2,at=c(seq(0,10,1)), labels=c(seq(0,10,1)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"))
# segments(0.7, WCX18groupsize$avg[1] - WCX18groupsize$se[1], 0.7, 
#          WCX18groupsize$avg[1] + WCX18groupsize$se[1], lwd = 1)
# arrows(0.7, WCX18groupsize$avg[1] - WCX18groupsize$se[1], 0.7,
#       WCX18groupsize$avg[1] + WCX18groupsize$se[1], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(1.9, WCX18groupsize$avg[2] - WCX18groupsize$se[2], 1.9, 
#          WCX18groupsize$avg[2] + WCX18groupsize$se[2], lwd = 1)
# arrows(1.9, WCX18groupsize$avg[2] - WCX18groupsize$se[2], 1.9,
#       WCX18groupsize$avg[2] + WCX18groupsize$se[2], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# segments(3.1, WCX18groupsize$avg[3] - WCX18groupsize$se[3], 3.1, 
#          WCX18groupsize$avg[3] + WCX18groupsize$se[3], lwd = 1)
# arrows(3.1, WCX18groupsize$avg[3] - WCX18groupsize$se[3], 3.1,
#       WCX18groupsize$avg[3] + WCX18groupsize$se[3], lwd = 1, angle = 90, code = 3, length = 0.05)
# 
# mtext(expression(paste("Number of Individuals", " ± SE")), 2, las = 0 , cex = 1, padj = -3)
# mtext("Average Group Size", 3, las = 0 , cex = 1, padj = 3)
# text(0.7, 2.25, "2", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 3.5, "3", pos = 3, cex = 0.75)
# dev.off()
```
***
### Multi Species Interactions
```{r}
# jpeg(filename = "figures/multi/BGT18_Multi.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGT18multi$freq,
#         col = viridis(6),
#         main = "Boggy Creek Trail 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 400))
# axis(2,at=c(seq(0, 400, 50)), labels=c(seq(0, 400, 50)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7), labels = c("Horse/Cow", "Horse/Elk", "Cow/Elk", "Horse/Deer", "Elk/Deer", "Elk/Pronghorn"), cex.axis = 0.75)
# mtext("Number of Interactions", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 0, "0", pos = 3, cex = 0.75)
# text(1.9, 19, "19", pos = 3, cex = 0.75)
# text(3.1, 0, "0", pos = 3, cex = 0.75)
# text(4.3, 0, "0", pos = 3, cex = 0.75)
# text(5.5, 0, "0", pos = 3, cex = 0.75)
# text(6.7, 0, "0", pos = 3, cex = 0.75)
# dev.off()
```

```{r}
# jpeg(filename = "figures/multi/BGW17_Multi.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGW17multi$freq,
#         col = viridis(6),
#         main = "Boggy Creek Timelapse 2017",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 400))
# axis(2,at=c(seq(0, 400, 50)), labels=c(seq(0, 400, 50)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7), labels = c("Horse/Cow", "Horse/Elk", "Cow/Elk", "Horse/Deer", "Elk/Deer", "Elk/Pronghorn"), cex.axis = 0.75)
# mtext("Number of Interactions", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 55, "55", pos = 3, cex = 0.75)
# text(1.9, 33, "33", pos = 3, cex = 0.75)
# text(3.1, 0, "0", pos = 3, cex = 0.75)
# text(4.3, 0, "0", pos = 3, cex = 0.75)
# text(5.5, 0, "0", pos = 3, cex = 0.75)
# text(6.7, 0, "0", pos = 3, cex = 0.75)
# dev.off()
```

```{r}
# jpeg(filename = "figures/multi/BGW18_Multi.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGW18multi$freq,
#         col = viridis(6),
#         main = "Boggy Creek Timelapse 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 400))
# axis(2,at=c(seq(0, 400, 50)), labels=c(seq(0, 400, 50)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7), labels = c("Horse/Cow", "Horse/Elk", "Cow/Elk", "Horse/Deer", "Elk/Deer", "Elk/Pronghorn"), cex.axis = 0.75)
# mtext("Number of Interactions", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 0, "0", pos = 3, cex = 0.75)
# text(1.9, 34, "34", pos = 3, cex = 0.75)
# text(3.1, 0, "0", pos = 3, cex = 0.75)
# text(4.3, 0, "0", pos = 3, cex = 0.75)
# text(5.5, 0, "0", pos = 3, cex = 0.75)
# text(6.7, 0, "0", pos = 3, cex = 0.75)
# dev.off()
```

```{r}
# jpeg(filename = "figures/multi/BGX18_Multi.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGX18multi$freq,
#         col = viridis(6),
#         main = "Boggy Creek Exclosure 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 400))
# axis(2,at=c(seq(0, 400, 50)), labels=c(seq(0, 400, 50)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7), labels = c("Horse/Cow", "Horse/Elk", "Cow/Elk", "Horse/Deer", "Elk/Deer", "Elk/Pronghorn"), cex.axis = 0.75)
# mtext("Number of Interactions", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 0, "0", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 0, "0", pos = 3, cex = 0.75)
# text(4.3, 0, "0", pos = 3, cex = 0.75)
# text(5.5, 0, "0", pos = 3, cex = 0.75)
# text(6.7, 0, "0", pos = 3, cex = 0.75)
# dev.off()
```

```{r}
# jpeg(filename = "figures/multi/WCS17_Multi.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCS17multi$freq,
#         col = viridis(6),
#         main = "Wildcat Creek Timelapse 2017",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 400))
# axis(2,at=c(seq(0, 400, 50)), labels=c(seq(0, 400, 50)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7), labels = c("Horse/Cow", "Horse/Elk", "Cow/Elk", "Horse/Deer", "Elk/Deer", "Elk/Pronghorn"), cex.axis = 0.75)
# mtext("Number of Interactions", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 341, "341", pos = 3, cex = 0.75)
# text(1.9, 140, "140", pos = 3, cex = 0.75)
# text(3.1, 110, "110", pos = 3, cex = 0.75)
# text(4.3, 31, "31", pos = 3, cex = 0.75)
# text(5.5, 19, "19", pos = 3, cex = 0.75)
# text(6.7, 6, "6", pos = 3, cex = 0.75)
# dev.off()
```

```{r}
# jpeg(filename = "figures/multi/WCS18_Multi.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCS18multi$freq,
#         col = viridis(6),
#         main = "Wildcat Creek Timelapse 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 400))
# axis(2,at=c(seq(0, 400, 50)), labels=c(seq(0, 400, 50)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7), labels = c("Horse/Cow", "Horse/Elk", "Cow/Elk", "Horse/Deer", "Elk/Deer", "Elk/Pronghorn"), cex.axis = 0.75)
# mtext("Number of Interactions", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 11, "11", pos = 3, cex = 0.75)
# text(1.9, 116, "116", pos = 3, cex = 0.75)
# text(3.1, 15, "15", pos = 3, cex = 0.75)
# text(4.3, 0, "0", pos = 3, cex = 0.75)
# text(5.5, 0, "0", pos = 3, cex = 0.75)
# text(6.7, 8, "8", pos = 3, cex = 0.75)
# dev.off()
```

```{r}
# jpeg(filename = "figures/multi/WCT18_Multi.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCT18multi$freq,
#         col = viridis(6),
#         main = "Wildcat Creek Trail 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1,
#         ylim = c(0, 400))
# axis(2,at=c(seq(0, 400, 50)), labels=c(seq(0, 400, 50)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7), labels = c("Horse/Cow", "Horse/Elk", "Cow/Elk", "Horse/Deer", "Elk/Deer", "Elk/Pronghorn"), cex.axis = 0.75)
# mtext("Number of Interactions", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 0, "0", pos = 3, cex = 0.75)
# text(1.9, 7, "7", pos = 3, cex = 0.75)
# text(3.1, 0, "0", pos = 3, cex = 0.75)
# text(4.3, 0, "0", pos = 3, cex = 0.75)
# text(5.5, 0, "0", pos = 3, cex = 0.75)
# text(6.7, 3, "3", pos = 3, cex = 0.75)
# dev.off()
```

```{r}
# jpeg(filename = "figures/multi/WCX18_Multi.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCX18multi$freq,
#         col = viridis(6),
#         main = "Wildcat Creek Exclosure 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 400))
# axis(2,at=c(seq(0, 400, 50)), labels=c(seq(0, 400, 50)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1, 4.3, 5.5, 6.7), labels = c("Horse/Cow", "Horse/Elk", "Cow/Elk", "Horse/Deer", "Elk/Deer", "Elk/Pronghorn"), cex.axis = 0.75)
# mtext("Number of Interactions", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 0, "0", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 0, "0", pos = 3, cex = 0.75)
# text(4.3, 0, "0", pos = 3, cex = 0.75)
# text(5.5, 0, "0", pos = 3, cex = 0.75)
# text(6.7, 0, "0", pos = 3, cex = 0.75)
# dev.off()
```
***
### Use of Waterway

```{r}
# jpeg(filename = "figures/waterway/BGT18_Waterway.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGT18water$n,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Trail 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 1100))
# axis(2,at=c(seq(0, 1100, 100)), labels=c(seq(0, 1100, 100)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Detections in the Waterway", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 337, "337", pos = 3, cex = 0.75)
# text(1.9, 9, "9", pos = 3, cex = 0.75)
# text(3.1, 31, "31", pos = 3, cex = 0.75)
# dev.off()
```
***
### Boggy Creek Timelapse 2017
```{r}
# jpeg(filename = "figures/waterway/BGW17_Waterway.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGW17water$n,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Timelapse 2017",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 1100))
# axis(2,at=c(seq(0, 1100, 100)), labels=c(seq(0, 1100, 100)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Detections in the Waterway", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 785, "785", pos = 3, cex = 0.75)
# text(1.9, 179, "179", pos = 3, cex = 0.75)
# text(3.1, 240, "240", pos = 3, cex = 0.75)
# dev.off()
```
***
### Boggy Creek Timelapse 2018
```{r}
# jpeg(filename = "figures/waterway/BGW18_Waterway.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGW18water$n,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Timelapse 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1, 
#         ylim = c(0, 1100))
# axis(2,at=c(seq(0, 1100, 100)), labels=c(seq(0, 1100, 100)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Detections in the Waterway", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 550, "550", pos = 3, cex = 0.75)
# text(1.9, 12, "12", pos = 3, cex = 0.75)
# text(3.1, 83, "83", pos = 3, cex = 0.75)
# dev.off()
```
***
### Boggy Creek Exclosure 2018
```{r}
# jpeg(filename = "figures/waterway/BGX18_Waterway.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(BGX18water$n,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Boggy Creek Exclosure 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1,
#         ylim = c(0, 1100))
# axis(2,at=c(seq(0, 1100, 100)), labels=c(seq(0, 1100, 100)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Detections in the Waterway", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 0, "0", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 0, "0", pos = 3, cex = 0.75)
# dev.off()
```
***
### Wildcat Creek Timelapse 2017
```{r}
# jpeg(filename = "figures/waterway/WCS17_Waterway.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCS17water$n,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Timelapse 2017",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1,
#         ylim = c(0, 1100))
# axis(2,at=c(seq(0, 1100, 100)), labels=c(seq(0, 1100, 100)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Detections in the Waterway", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 1009, "1009", pos = 3, cex = 0.75)
# text(1.9, 675, "675", pos = 3, cex = 0.75)
# text(3.1, 644, "644", pos = 3, cex = 0.75)
# dev.off()
```
***
### Wildcat Creek Timelapse 2018
```{r}
# jpeg(filename = "figures/waterway/WCS18_Waterway.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCS18water$n,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Timelapse 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1,
#         ylim = c(0, 1100))
# axis(2,at=c(seq(0, 1100, 100)), labels=c(seq(0, 1100, 100)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Detections in the Waterway", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 540, "540", pos = 3, cex = 0.75)
# text(1.9, 546, "546", pos = 3, cex = 0.75)
# text(3.1, 93, "93", pos = 3, cex = 0.75)
# dev.off()
```
***
### Wildcat Creek Trail 2018
```{r}
# jpeg(filename = "figures/waterway/WCT18_Waterway.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCT18water$n,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Trail 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1,
#         ylim = c(0, 1100))
# axis(2,at=c(seq(0, 1100, 100)), labels=c(seq(0, 1100, 100)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Detections in the Waterway", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 10, "10", pos = 3, cex = 0.75)
# text(1.9, 54, "54", pos = 3, cex = 0.75)
# text(3.1, 2, "2", pos = 3, cex = 0.75)
# dev.off()
```
***
### Wildcat Creek Exclosure 2018
```{r}
# jpeg(filename = "figures/waterway/WCX18_Waterway.jpg",
#      width=6.5,
#      height=6.5,
#      units="in",
#      res=300)
# plot.new()
# # bottom, left, top, right
# par(mar=c(3, 4, 2, 2))
# barplot(WCX18water$n,
#         col = c("#4472C4", "#ED7D31", "#FFC000"),
#         main = "Wildcat Creek Exclosure 2018",
#         axes = FALSE,
#         cex.lab = 1,
#         cex.main = 1,
#         ylim = c(0, 1100))
# axis(2,at=c(seq(0, 1100, 100)), labels=c(seq(0, 1100, 100)), cex.axis= 0.5, las = 2)
# axis(1, at = c(0.7, 1.9, 3.1), labels = c("Horses", "Cattle", "Elk"), cex.axis = 0.75)
# mtext("Number of Detections in the Waterway", 2, las = 0 , cex = 1, padj = -4)
# text(0.7, 204, "204", pos = 3, cex = 0.75)
# text(1.9, 0, "0", pos = 3, cex = 0.75)
# text(3.1, 112, "112", pos = 3, cex = 0.75)
# dev.off()
```
***
### Behavior
#### Boggy Creek Trail 2018
```{r}
jpeg(filename = "figures/behavior/BGT18_behav.jpg",
     width=6.5,
     height=6.5,
     units="in",
     res=300)
plot.new()
barplot(BGT18behav,
        main = "Boggy Creek Trail 2018",
        ylim = c(0, 100),
        ylab = "Percent of Total Observed Behaviors",
        border = "black",
        col = c("#4472C4", "#ED7D31", "#FFC000"),
        beside = TRUE,
        legend = rownames(BGT18behav),
        axes =  FALSE)
axis(2,at=c(seq(0, 100, 10)), labels=c(seq(0, 100, 10)), cex.axis= 0.5, las = 2)

text(1.75, BGT18h_behav$percent[1]+2, BGT18h_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(2.75, BGT18c_behav$percent[1]+2, BGT18c_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(3.75, BGT18e_behav$percent[1]+2, BGT18e_behav$percent[1], pos = 3, cex = 0.75, srt = 90)

text(5.75, BGT18h_behav$percent[2]+2, BGT18h_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(6.75, BGT18c_behav$percent[2]+2, BGT18c_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(7.75, BGT18e_behav$percent[2]+2, BGT18e_behav$percent[2], pos = 3, cex = 0.75, srt = 90)

text(9.75, BGT18h_behav$percent[3]+2, BGT18h_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(10.75, BGT18c_behav$percent[3]+2, BGT18c_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(11.75, BGT18e_behav$percent[3]+2, BGT18e_behav$percent[3], pos = 3, cex = 0.75, srt = 90)

text(13.75, BGT18h_behav$percent[4]+2, BGT18h_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(14.75, BGT18c_behav$percent[4]+2, BGT18c_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(15.75, BGT18e_behav$percent[4]+2, BGT18e_behav$percent[4], pos = 3, cex = 0.75, srt = 90)

text(17.75, BGT18h_behav$percent[5]+2, BGT18h_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(18.75, BGT18c_behav$percent[5]+2, BGT18c_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(19.75, BGT18e_behav$percent[5]+2, BGT18e_behav$percent[5], pos = 3, cex = 0.75, srt = 90)

text(21.75, BGT18h_behav$percent[6]+2, BGT18h_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(22.75, BGT18c_behav$percent[6]+2, BGT18c_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(23.75, BGT18e_behav$percent[6]+2, BGT18e_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
dev.off()
```
***
#### Boggy Creek Timelapse 2017 Behavioral Frequency
```{r}
jpeg(filename = "figures/behavior/BGW17_behav.jpg",
     width=6.5,
     height=6.5,
     units="in",
     res=300)
plot.new()
barplot(BGW17behav,
        main = "Boggy Creek Timelapse 2017",
        ylim = c(0, 100),
        ylab = "Percent of Total Observed Behaviors",
        border = "black",
        col = c("#4472C4", "#ED7D31", "#FFC000"),
        beside = TRUE,
        legend = rownames(BGW17behav),
        axes =  FALSE)
axis(2,at=c(seq(0, 100, 10)), labels=c(seq(0, 100, 10)), cex.axis= 0.5, las = 2)

text(1.75, BGW17h_behav$percent[1]+2, BGW17h_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(2.75, BGW17c_behav$percent[1]+2, BGW17c_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(3.75, BGW17e_behav$percent[1]+2, BGW17e_behav$percent[1], pos = 3, cex = 0.75, srt = 90)

text(5.75, BGW17h_behav$percent[2]+2, BGW17h_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(6.75, BGW17c_behav$percent[2]+2, BGW17c_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(7.75, BGW17e_behav$percent[2]+2, BGW17e_behav$percent[2], pos = 3, cex = 0.75, srt = 90)

text(9.75, BGW17h_behav$percent[3]+2, BGW17h_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(10.75, BGW17c_behav$percent[3]+2, BGW17c_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(11.75, BGW17e_behav$percent[3]+2, BGW17e_behav$percent[3], pos = 3, cex = 0.75, srt = 90)

text(13.75, BGW17h_behav$percent[4]+2, BGW17h_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(14.75, BGW17c_behav$percent[4]+2, BGW17c_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(15.75, BGW17e_behav$percent[4]+2, BGW17e_behav$percent[4], pos = 3, cex = 0.75, srt = 90)

text(17.75, BGW17h_behav$percent[5]+2, BGW17h_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(18.75, BGW17c_behav$percent[5]+2, BGW17c_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(19.75, BGW17e_behav$percent[5]+2, BGW17e_behav$percent[5], pos = 3, cex = 0.75, srt = 90)

text(21.75, BGW17h_behav$percent[6]+2, BGW17h_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(22.75, BGW17c_behav$percent[6]+2, BGW17c_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(23.75, BGW17e_behav$percent[6]+2, BGW17e_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
dev.off()
```
***
#### Boggy Creek Timelapse 2018 Behavioral Frequency
```{r}
jpeg(filename = "figures/behavior/BGW18_behav.jpg",
     width=6.5,
     height=6.5,
     units="in",
     res=300)
plot.new()
barplot(BGW18behav,
        main = "Boggy Creek Timelapse 2018",
        ylim = c(0, 100),
        ylab = "Percent of Total Observed Behaviors",
        border = "black",
        col = c("#4472C4", "#ED7D31", "#FFC000"),
        beside = TRUE,
        legend = rownames(BGW18behav),
        axes =  FALSE)
axis(2,at=c(seq(0, 100, 10)), labels=c(seq(0, 100, 10)), cex.axis= 0.5, las = 2)

text(1.75, BGW18h_behav$percent[1]+2, BGW18h_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(2.75, BGW18c_behav$percent[1]+2, BGW18c_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(3.75, BGW18e_behav$percent[1]+2, BGW18e_behav$percent[1], pos = 3, cex = 0.75, srt = 90)

text(5.75, BGW18h_behav$percent[2]+2, BGW18h_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(6.75, BGW18c_behav$percent[2]+2, BGW18c_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(7.75, BGW18e_behav$percent[2]+2, BGW18e_behav$percent[2], pos = 3, cex = 0.75, srt = 90)

text(9.75, BGW18h_behav$percent[3]+2, BGW18h_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(10.75, BGW18c_behav$percent[3]+2, BGW18c_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(11.75, BGW18e_behav$percent[3]+2, BGW18e_behav$percent[3], pos = 3, cex = 0.75, srt = 90)

text(13.75, BGW18h_behav$percent[4]+2, BGW18h_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(14.75, BGW18c_behav$percent[4]+2, BGW18c_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(15.75, BGW18e_behav$percent[4]+2, BGW18e_behav$percent[4], pos = 3, cex = 0.75, srt = 90)

text(17.75, BGW18h_behav$percent[5]+2, BGW18h_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(18.75, BGW18c_behav$percent[5]+2, BGW18c_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(19.75, BGW18e_behav$percent[5]+2, BGW18e_behav$percent[5], pos = 3, cex = 0.75, srt = 90)

text(21.75, BGW18h_behav$percent[6]+2, BGW18h_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(22.75, BGW18c_behav$percent[6]+2, BGW18c_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(23.75, BGW18e_behav$percent[6]+2, BGW18e_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
dev.off()
```
***
### Boggy Creek Exclosure 2018
```{r}
jpeg(filename = "figures/behavior/BGX18_behav.jpg",
     width=6.5,
     height=6.5,
     units="in",
     res=300)
plot.new()
barplot(BGX18behav,
        main = "Boggy Creek Exclosure 2018",
        ylim = c(0, 100),
        ylab = "Percent of Total Observed Behaviors",
        border = "black",
        col = c("#4472C4", "#ED7D31", "#FFC000"),
        beside = TRUE,
        legend = rownames(BGX18behav),
        axes =  FALSE)
axis(2,at=c(seq(0, 100, 10)), labels=c(seq(0, 100, 10)), cex.axis= 0.5, las = 2)

text(1.75, BGX18h_behav$percent[1]+2, BGX18h_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(2.75, BGX18c_behav$percent[1]+2, BGX18c_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(3.75, BGX18e_behav$percent[1]+2, BGX18e_behav$percent[1], pos = 3, cex = 0.75, srt = 90)

text(5.75, BGX18h_behav$percent[2]+2, BGX18h_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(6.75, BGX18c_behav$percent[2]+2, BGX18c_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(7.75, BGX18e_behav$percent[2]+2, BGX18e_behav$percent[2], pos = 3, cex = 0.75, srt = 90)

text(9.75, BGX18h_behav$percent[3]+2, BGX18h_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(10.75, BGX18c_behav$percent[3]+2, BGX18c_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(11.75, BGX18e_behav$percent[3]+2, BGX18e_behav$percent[3], pos = 3, cex = 0.75, srt = 90)

text(13.75, BGX18h_behav$percent[4]+2, BGX18h_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(14.75, BGX18c_behav$percent[4]+2, BGX18c_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(15.75, BGX18e_behav$percent[4]+2, BGX18e_behav$percent[4], pos = 3, cex = 0.75, srt = 90)

text(17.75, BGX18h_behav$percent[5]+2, BGX18h_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(18.75, BGX18c_behav$percent[5]+2, BGX18c_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(19.75, BGX18e_behav$percent[5]+2, BGX18e_behav$percent[5], pos = 3, cex = 0.75, srt = 90)

text(21.75, BGX18h_behav$percent[6]+2, BGX18h_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(22.75, BGX18c_behav$percent[6]+2, BGX18c_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(23.75, BGX18e_behav$percent[6]+2, BGX18e_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
dev.off()
```
***
#### Wildcat Creek Timelapse Behavioral Frequency
```{r}
jpeg(filename = "figures/behavior/WCS17_behav.jpg",
     width=6.5,
     height=6.5,
     units="in",
     res=300)
plot.new()
barplot(WCS17behav,
        main = "Wildcat Creek Timelapse 2017",
        ylim = c(0, 100),
        ylab = "Percent of Total Observed Behaviors",
        border = "black",
        col = c("#4472C4", "#ED7D31", "#FFC000"),
        beside = TRUE,
        legend = rownames(WCS17behav),
        axes =  FALSE)
axis(2,at=c(seq(0, 100, 10)), labels=c(seq(0, 100, 10)), cex.axis= 0.5, las = 2)

text(1.75, WCS17h_behav$percent[1]+2, WCS17h_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(2.75, WCS17c_behav$percent[1]+2, WCS17c_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(3.75, WCS17e_behav$percent[1]+2, WCS17e_behav$percent[1], pos = 3, cex = 0.75, srt = 90)

text(5.75, WCS17h_behav$percent[2]+2, WCS17h_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(6.75, WCS17c_behav$percent[2]+2, WCS17c_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(7.75, WCS17e_behav$percent[2]+2, WCS17e_behav$percent[2], pos = 3, cex = 0.75, srt = 90)

text(9.75, WCS17h_behav$percent[3]+2, WCS17h_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(10.75, WCS17c_behav$percent[3]+2, WCS17c_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(11.75, WCS17e_behav$percent[3]+2, WCS17e_behav$percent[3], pos = 3, cex = 0.75, srt = 90)

text(13.75, WCS17h_behav$percent[4]+2, WCS17h_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(14.75, WCS17c_behav$percent[4]+2, WCS17c_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(15.75, WCS17e_behav$percent[4]+2, WCS17e_behav$percent[4], pos = 3, cex = 0.75, srt = 90)

text(17.75, WCS17h_behav$percent[5]+2, WCS17h_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(18.75, WCS17c_behav$percent[5]+2, WCS17c_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(19.75, WCS17e_behav$percent[5]+2, WCS17e_behav$percent[5], pos = 3, cex = 0.75, srt = 90)

text(21.75, WCS17h_behav$percent[6]+2, WCS17h_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(22.75, WCS17c_behav$percent[6]+2, WCS17c_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(23.75, WCS17e_behav$percent[6]+2, WCS17e_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
dev.off()
```
***
#### Wildcat Creek Timelapse 2018 Behavioral Frequency
```{r}
jpeg(filename = "figures/behavior/WCS18_behav.jpg",
     width=6.5,
     height=6.5,
     units="in",
     res=300)
plot.new()
barplot(WCS18behav,
        main = "Wildcat Creek Timelapse 2018",
        ylim = c(0, 100),
        ylab = "Percent of Total Observed Behaviors",
        border = "black",
        col = c("#4472C4", "#ED7D31", "#FFC000"),
        beside = TRUE,
        legend = rownames(WCS18behav),
        axes =  FALSE)
axis(2,at=c(seq(0, 100, 10)), labels=c(seq(0, 100, 10)), cex.axis= 0.5, las = 2)

text(1.75, WCS18h_behav$percent[1]+2, WCS18h_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(2.75, WCS18c_behav$percent[1]+2, WCS18c_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(3.75, WCS18e_behav$percent[1]+2, WCS18e_behav$percent[1], pos = 3, cex = 0.75, srt = 90)

text(5.75, WCS18h_behav$percent[2]+2, WCS18h_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(6.75, WCS18c_behav$percent[2]+2, WCS18c_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(7.75, WCS18e_behav$percent[2]+2, WCS18e_behav$percent[2], pos = 3, cex = 0.75, srt = 90)

text(9.75, WCS18h_behav$percent[3]+2, WCS18h_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(10.75, WCS18c_behav$percent[3]+2, WCS18c_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(11.75, WCS18e_behav$percent[3]+2, WCS18e_behav$percent[3], pos = 3, cex = 0.75, srt = 90)

text(13.75, WCS18h_behav$percent[4]+2, WCS18h_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(14.75, WCS18c_behav$percent[4]+2, WCS18c_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(15.75, WCS18e_behav$percent[4]+2, WCS18e_behav$percent[4], pos = 3, cex = 0.75, srt = 90)

text(17.75, WCS18h_behav$percent[5]+2, WCS18h_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(18.75, WCS18c_behav$percent[5]+2, WCS18c_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(19.75, WCS18e_behav$percent[5]+2, WCS18e_behav$percent[5], pos = 3, cex = 0.75, srt = 90)

text(21.75, WCS18h_behav$percent[6]+2, WCS18h_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(22.75, WCS18c_behav$percent[6]+2, WCS18c_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(23.75, WCS18e_behav$percent[6]+2, WCS18e_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
dev.off()
```
***
#### Wildcat Creek Trail 2018 Behavioral Frequency
```{r}
jpeg(filename = "figures/behavior/WCT18_behav.jpg",
     width=6.5,
     height=6.5,
     units="in",
     res=300)
plot.new()
barplot(WCT18behav,
        main = "Wildcat Creek Trail 2018",
        ylim = c(0, 100),
        ylab = "Percent of Total Observed Behaviors",
        border = "black",
        col = c("#4472C4", "#ED7D31", "#FFC000"),
        beside = TRUE,
        legend = rownames(WCT18behav),
        axes =  FALSE)
axis(2,at=c(seq(0, 100, 10)), labels=c(seq(0, 100, 10)), cex.axis= 0.5, las = 2)

text(1.75, WCT18h_behav$percent[1]+2, WCT18h_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(2.75, WCT18c_behav$percent[1]+2, WCT18c_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(3.75, WCT18e_behav$percent[1]+2, WCT18e_behav$percent[1], pos = 3, cex = 0.75, srt = 90)

text(5.75, WCT18h_behav$percent[2]+2, WCT18h_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(6.75, WCT18c_behav$percent[2]+2, WCT18c_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(7.75, WCT18e_behav$percent[2]+2, WCT18e_behav$percent[2], pos = 3, cex = 0.75, srt = 90)

text(9.75, WCT18h_behav$percent[3]+2, WCT18h_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(10.75, WCT18c_behav$percent[3]+2, WCT18c_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(11.75, WCT18e_behav$percent[3]+2, WCT18e_behav$percent[3], pos = 3, cex = 0.75, srt = 90)

text(13.75, WCT18h_behav$percent[4]+2, WCT18h_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(14.75, WCT18c_behav$percent[4]+2, WCT18c_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(15.75, WCT18e_behav$percent[4]+2, WCT18e_behav$percent[4], pos = 3, cex = 0.75, srt = 90)

text(17.75, WCT18h_behav$percent[5]+2, WCT18h_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(18.75, WCT18c_behav$percent[5]+2, WCT18c_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(19.75, WCT18e_behav$percent[5]+2, WCT18e_behav$percent[5], pos = 3, cex = 0.75, srt = 90)

text(21.75, WCT18h_behav$percent[6]+2, WCT18h_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(22.75, WCT18c_behav$percent[6]+2, WCT18c_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(23.75, WCT18e_behav$percent[6]+2, WCT18e_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
dev.off()
```
***
#### Wildcat Creek Exclosure 2018 Behavioral Frequency
```{r}
jpeg(filename = "figures/behavior/WCX18_behav.jpg",
     width=6.5,
     height=6.5,
     units="in",
     res=300)
plot.new()
barplot(WCX18behav,
        main = "Wildcat Creek Exclosure 2018",
        ylim = c(0, 100),
        ylab = "Percent of Total Observed Behaviors",
        border = "black",
        col = c("#4472C4", "#ED7D31", "#FFC000"),
        beside = TRUE,
        legend = rownames(WCX18behav),
        axes =  FALSE)
axis(2,at=c(seq(0, 100, 10)), labels=c(seq(0, 100, 10)), cex.axis= 0.5, las = 2)

text(1.75, WCX18h_behav$percent[1]+2, WCX18h_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(2.75, WCX18c_behav$percent[1]+2, WCX18c_behav$percent[1], pos = 3, cex = 0.75, srt = 90)
text(3.75, WCX18e_behav$percent[1]+2, WCX18e_behav$percent[1], pos = 3, cex = 0.75, srt = 90)

text(5.75, WCX18h_behav$percent[2]+2, WCX18h_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(6.75, WCX18c_behav$percent[2]+2, WCX18c_behav$percent[2], pos = 3, cex = 0.75, srt = 90)
text(7.75, WCX18e_behav$percent[2]+2, WCX18e_behav$percent[2], pos = 3, cex = 0.75, srt = 90)

text(9.75, WCX18h_behav$percent[3]+2, WCX18h_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(10.75, WCX18c_behav$percent[3]+2, WCX18c_behav$percent[3], pos = 3, cex = 0.75, srt = 90)
text(11.75, WCX18e_behav$percent[3]+2, WCX18e_behav$percent[3], pos = 3, cex = 0.75, srt = 90)

text(13.75, WCX18h_behav$percent[4]+2, WCX18h_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(14.75, WCX18c_behav$percent[4]+2, WCX18c_behav$percent[4], pos = 3, cex = 0.75, srt = 90)
text(15.75, WCX18e_behav$percent[4]+2, WCX18e_behav$percent[4], pos = 3, cex = 0.75, srt = 90)

text(17.75, WCX18h_behav$percent[5]+2, WCX18h_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(18.75, WCX18c_behav$percent[5]+2, WCX18c_behav$percent[5], pos = 3, cex = 0.75, srt = 90)
text(19.75, WCX18e_behav$percent[5]+2, WCX18e_behav$percent[5], pos = 3, cex = 0.75, srt = 90)

text(21.75, WCX18h_behav$percent[6]+2, WCX18h_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(22.75, WCX18c_behav$percent[6]+2, WCX18c_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
text(23.75, WCX18e_behav$percent[6]+2, WCX18e_behav$percent[6], pos = 3, cex = 0.75, srt = 90)
dev.off()
```